---
title: "Untitled"
author: "Jonathan Bourne"
date: "5 July 2017"
output: html_document
---


Islington should be removed and put back in when they send the correct data, it is giving a false negative

Should type B be included? or just type A?

```{r setup}
setwd( "~/Dropbox/SSE/Empty Homes/EmptyHomesCode/SubCode")
source("Setup.R")

setwd(Functions)
list.files() %>% map(source)

Figures <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Empty Homes Write up/Figures"
```



```{r}
source(file.path(CommonCode, "AuxdataLoad.R"))
```


#Cumbria
```{r}
setwd(file.path(RegionsComp, "Region North West"))

BarrowCUMBRIADATA <- read_excel("Barrow-in-FurnessExemptionsLSOA.xlsx", sheet=1)[1:4]%>%  
  StructureData(.,lowuse = c(2:6,8))

SLakelandCUMBRIADATA <- read_excel("South LakelandExemptionsLSOA.XLSX", sheet=1)[,1:4] %>%
    StructureData(., lowuse=2:9)

#only inlcudes postcodes so the mergeing needs to be done manually
CopelandCUMBRIADATA <- read_excel("CopelandFOI 5778 data 100517 CBC.XLSX", sheet=1) %>% 
  mutate(Postcode = sub(" ", "", Postcode)) %>%
  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=`Disc Type Ind`, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
  StructureData()


EdenCUMBRIADATA <- read_excel("EdenDiscountsLSOA.xlsx"  , sheet=1)[1:4] %>%  
  StructureData(.,lowuse = c(2:6,8))

CarliseCUMBRIADATA <- read_excel("FOI 5846 5983-CarlisleDiscountsLSOA June 2017.xlsx"  , sheet=1)[1:4] %>%  
  StructureData(.)

```


#Manchester

```{r}
list.files()

OldhamMANCDATA <- read_excel("FOI 10635 OldhamDiscounts LSOA.xlsx", sheet = 1 )[c(1,4:6)] %>%  
  StructureData(., c(5:6,8:11))

ManchesterMANCDATA <- read_excel("ManchesterDiscountsLSOA.xlsx", sheet = 1 )[1:4] %>%  
  StructureData(. )

RochdaleMANCDATA <- read_excel("Rochdale Both.xlsx" , sheet = 1 )[1:4] %>%  
  StructureData(., c(5,6,14,15,20:22))

TamesideMANCDATA <- read_excel("Tameside FOI 6257A2.xlsx", sheet = 1 )[1:4] %>%  
  StructureData(. )

TraffordMANCDATA <- read_excel("Trafford Exemption and Levy.xlsx" , sheet = 1 )[1:4] %>%
  filter(Exemption_type =="LEVY") %>% 
  bind_rows(.,read_excel("TraffordDiscountsLSOA.XLSX", sheet = 1 )[1:4] %>% rename(Exemption_type = Class)) %>%
  StructureData()

WiganMANCDATA <- read_excel("Wigan 5528 DISCOUNTS.xlsx", sheet = 1 )[1:4] %>%  
  StructureData(., lowuse = c(2:3, 5:9) )

ls(pattern = "MANC") %>% map_df(~eval(parse(text=.x))) %>% PlotMap(., AG)


```


#Cornwall

```{r}

setwd(file.path(RegionsComp, "Region South West"))

CornwallDATA <- read_excel("Cornwall.xlsx", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
  StructureData(lowuse = c(2,23:28))
```

#Suffolk


```{r}
setwd(file.path(RegionsComp, "Region East of England"))
list.files()


#Serparete in to the two LADS
# CoastWaveDATA <- bind_rows(read.xlsx("FOI IMT178324 SuffolkCoastal.xlsx")[1:4] , read.xlsx("FOI IMT178324 Waveney.xlsx")[1:4]) %>% setNames(make.names(names(.))) %>%
#   mutate(Exemption.type = Exemption.type %>% trimws %>%
#            make.names %>% 
#            gsub("\\.{2,}" , ".", .))  %>%
#   StructureData(., lowuse = c(5,6,13,14,16:18))

CoastSUFFDATA <- read.xlsx("FOI IMT178324 SuffolkCoastal.xlsx")[1:4] %>% setNames(make.names(names(.))) %>%
  mutate(Exemption.type = Exemption.type %>% trimws %>%
           make.names %>% 
           gsub("\\.{2,}" , ".", .))  %>%
  StructureData(.,c(5,6,11,12,14:16))

WaveneySUFFDATA <- read.xlsx("FOI IMT178324 Waveney.xlsx")[1:4] %>% setNames(make.names(names(.))) %>%
  mutate(Exemption.type = Exemption.type %>% trimws %>%
           make.names %>% 
           gsub("\\.{2,}" , ".", .))  %>%
  StructureData(., lowuse = c(5,6,13,14,16:18))


```

#Norfolk
```{r}
#Broadlands is unsuable, due to lack of data collection.
#This is being checked
# BroadlandsDATA <- read_excel("BroadlandDiscountsLSOA.xlsx", sheet=1)[1:4] %>%
#   StructureData()

```


#Cambridge
```{r}
EastCambsDATA <- read_excel("EC FOI 130 - DISC_FOI_0_3944413b.xlsx", sheet=1)[1:4] %>%
  StructureData()

```

#Brightong and Hove


```{r}

setwd(file.path(RegionsComp, "Region South East"))
list.files()


BrightonDATA <- read_excel("Copy of Brighton and HoveDiscountsLSOA (4).xlsx", sheet=1)%>% .[,c(2,3:5)] %>%
  StructureData(lowuse = 2:8)

#MakeLeaflet(BrightonDATA)

```



#Yorkshire and the Humber
```{r}
setwd(file.path(RegionsComp, "Region Yorkshire and The Humber"))

#Hull

HullDATA <-read_excel("KINGSTON UPON HULL%2c CITY OFDISCOUNTSLSOA.XLSX")[-c(c(1:6)),1:4] %>%
  StructureData(.)

#Harrowgate

HarrogateDATA <-read_excel("Harrogate DiscountsExemptionsLSOA.xlsx" )[,1:4] %>%
  StructureData(.,3:10)


```

#Wales

```{r}

setwd(file.path(RegionsComp, "Region Wales"))
list.files()


CeredigionDATA <- read_excel("CTAX - Ceredigion Discounts LSOA.xlsx", sheet=1)%>% .[,1:4] %>%
  StructureData(lowuse =c(8:13,15))

MonmouthDATA <- read_excel("MCC Discounts Jul 17.xlsx", sheet=1)%>% .[,1:4] %>%
  StructureData(lowuse = c(4:8))

CarmarthenDATA <- read_excel("CarmarthenshireDiscountsLSOA.XLSX" , sheet=1)%>% .[,1:4] %>%
  StructureData(2:4)

```


# London using the full data

```{r}
#Source the code from another file as it is very long
source(file.path(CommonCode, "LondonFullProcesss.R"))

#MakeLeaflet(NewhamLONDATA)

```


#Semi data 

The LSOA will be assigned empty and low use homes by percentage

```{r}
#ward folder
setwd(SemiLondon)


wardnames <- EW2 %>% group_by(Admin_ward_code, WD16NM) %>% summarise(counts = n(), LAD11NM = first(LAD11NM), LAD11CD = first(LAD11CD)) %>% arrange(WD16NM)


#Wandsworth

WandsworthLONDDATA <- read_excel("wandsworth2.xlsx",  skip = 3 ) %>% select(1,3) %>% 
  group_by(`Ptc Wardname`) %>% summarise(Empty = sum(`Count Current Occupancy Discounts`)) %>% ungroup %>% 
  arrange(`Ptc Wardname`) %>% 
  filter(!is.na(`Ptc Wardname`)) %>% 
  bind_cols(., wardnames %>% filter(LAD11NM == "Wandsworth") %>% 
              select(Admin_ward_code)) %>%
  mutate(LowUse = Empty) %>%
  SemiDataStructure


#Merton

MertonLONDATA <- read_excel("merton1.xlsx" )[,-2] %>%setNames(make.names(names(.))) %>% slice(-1) %>% arrange(X__1) %>%
  filter(X__1 != "Norbury", X__1!="Nightingale", X__1 !="Stonecot") %>% 
    bind_cols(., wardnames %>% filter(LAD11NM == "Merton") %>% 
              select(Admin_ward_code)) %>%
  mutate(Empty =   Disc.Class.C.Vacant.dwelling + Disc.class.C.Long.term.empty + Premium.Levy, LowUse =  Disc.Class.A.Second.home + Disc.Class.B.second.home ) %>%
  SemiDataStructure

#Kingston

KingstonLONDATA <- read_excel("Kingston1.xlsx"  )%>% setNames(make.names(names(.))) %>%
  arrange(X__1) %>% slice(1:16) %>%
  bind_cols(., wardnames %>% filter(LAD11NM == "Kingston upon Thames") %>% 
              select(Admin_ward_code)) %>%
  mutate(Empty = Empty...Furnished..0.. + Empty.Homes.Premium + LONG.TERM.EMPTY..0.. + Structural.Repair..0.., LowUse = Empty + X2nd.Home..0..) %>%
  SemiDataStructure


#TowerHamlets
TowerLONDATA <- read_excel("Towerhamlets.xlsx")[,c(1,3)] %>% 
  filter(!is.na(DiscClass)) %>%
  group_by(Ward, DiscClass) %>%
  summarise(count = n()) %>% ungroup %>%
  spread(., key =DiscClass, value = count, fill = 0 ) %>% 
  mutate(Empty = rowSums(.[,4:8]), LowUse = B+BE+Empty) %>% 
  slice(c(1:13, 15:17, 14, 18:20)) %>%
   bind_cols(., wardnames %>% filter(grepl("Tower", LAD11NM))) %>%
  SemiDataStructure

```

General Stats
#UK population


```{r}

#number of LUPS and Total Homes
ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x))) %>% 
  filter(!is.na(LAD11NM)) %>%
  summarise(
           TotalLads = length(unique(LAD11CD)),
           LowUse = sum(LowUse, na.rm = T),
           Homes = sum(Homes, na.rm = T),
           PercHomes = Homes/sum(EW2$Homes),
           Population = sum(Pop, na.rm= T),
           Poperc = Population/sum(EW2$Pop))

#Percentage of EW LADS
length(ls(pattern = "DATA"))/(EW2$LAD11NM %>% unique %>% length())

#check which lads are present even though I don't have data due to postcode matching
#test <- ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x)))  %>% arrange(LAD11NM)
#unique(test$LAD11NM)

```


#Plot stuff
```{r}
x <-bind_rows(SouthwarkLONDATA, TowerDATA, LambethLONDATA, CoLLONDATA, NewhamLONDATA) %>% MakeLeaflet

z<- MakeLeaflet(MonmouthDATA)
z
# 
# saveWidget(z, file=file.path(basewd, "CeredigionDATA"), selfcontained = TRUE )

#testSouth <- DistribCompareBootstrapper(SouthwarkLONDATA, 1652, 1000)
testSouth %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100) %>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

ValueTtest(test)



```


#Bootstrap

Now all the data is loaded each LAD needs to be bootstrapped

```{r}

setwd(basewd)

#load full data
BootStrapRES <-LoadAddDistribCompare("BootStrapRES.rds")

#Include only full price standard purchases
BootStrapRESA <-LoadAddDistribCompare("BootStrapRES_A.rds", type = "A")

#Inlcude only transfers and Buy-to-let and purcheses to non-private individuals
BootStrapRESA <-LoadAddDistribCompare("BootStrapRES_B.rds", type = "B")

elementnames<- names(BootStrapRES)





```


#Investigating Ceredigion

Ceredigion has cheaper LUps even though it has areas with high LUP. When investigating I changed the classes to take account of the different pricing levels in the LAD. This made no difference. However re-running the bootstrapping including only A type purchases in the LAD gave the expected result of high LUP prices. What appeared to be happening was a lot of property was being transferred in unsual ways. 

```{r}


CeredPrice <- prices %>% 
  filter( grepl("W06000008", Admin_district_code)) %>%
  select(Admin_ward_code, lsoa11cd, Price =X2, X15) %>%
  #filter(X15 == "A") %>%
  mutate(class = cut(Price, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
                     labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
                     right = F),
         Price = as.numeric(Price)) 

CeredPrice2 <- CeredPrice %>%
  group_by(lsoa11cd, class) %>%
  summarise(Admin_ward_code = first(Admin_ward_code),
            LSOAcounts = n()) 

CeredPrice2 <- CeredPrice2  %>%
  group_by(Admin_ward_code, class) %>%
  summarise(counts = n()) %>%
  group_by(class) %>%
  mutate(ClassPercent = counts/sum(counts)) %>%
  ungroup %>% group_by(Admin_ward_code) %>%
  mutate(WardPercent = counts/sum(counts))%>%
  left_join(CeredPrice2,. ,by=c("Admin_ward_code", "class")) %>%
  rename(LSOA_CODE = lsoa11cd)

RBKCPrice <- prices %>% 
  filter( grepl("E09000020", Admin_district_code)) %>%
    select(Admin_ward_code, lsoa11cd, Price =X2, X15) %>%
  #filter(X15 == "A") %>%
  mutate(class = cut(Price, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
                     labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
                     right = F),
         Price = as.numeric(Price)) 

RBKCPrice2 <- RBKCPrice %>%
  group_by(lsoa11cd, class) %>%
  summarise(Admin_ward_code = first(Admin_ward_code),
            LSOAcounts = n()) 

RBKCPrice2 <- RBKCPrice  %>%
  group_by(Admin_ward_code, class) %>%
  summarise(counts = n()) %>%
  group_by(class) %>%
  mutate(ClassPercent = counts/sum(counts)) %>%
  ungroup %>% group_by(Admin_ward_code) %>%
  mutate(WardPercent = counts/sum(counts))%>%
  left_join(RBKCPrice2,. ,by=c("Admin_ward_code", "class")) %>%
  rename(LSOA_CODE = lsoa11cd)

RBKCtot <- RBKCPrice2 %>%
  group_by(class) %>%
  summarise(counts = sum(counts))


summary(CeredPrice$Price)
summary(RBKCPrice$Price)

CeredBootAnorm <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, type = "A" )
CeredBootAB <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, c(0, 60, 120, 200, 500, Inf)*10^3 )

CeredBootA <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, c(0, 60, 120, 200, 500, Inf)*10^3, type = "A" )


ValueTtest(CeredBootAB)
ValueTtest(CeredBootA)
ValueTtest(CeredBootAnorm)

CeredBootAB %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

CeredBootA %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

CeredBootAnorm %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

RBKCPrice %>% group_by(X15) %>%
  summarise(mean = mean(Price))

CeredPrice %>% group_by(X15) %>%
  summarise(mean = mean(Price))

 RBKCPrice2 %>%
   filter(class == "Prime") %>%
   PlotMap(.,AG,  "ClassPercent")

  CeredPrice2 %>%
   filter(class == "Mid") %>%
   PlotMap(.,filter(AG, LAD11CD=="W06000008"), variable = "ClassPercent", filtermap = FALSE)
 
```

#Analyse Boostrap

```{r}



#Perform the t-test on the resulting lists
TtestRESgreater <-BootStrapRES %>% map(~ValueTtest(.x))
TtestREStwo.sided <-BootStrapRES %>% map(~ValueTtest(.x, alternative = "two.sided"))
#Tidy results of thejust the ttest
TtestRES2 <- TtestRESgreater %>% map_df(~.x$t.test %>% tidy) %>%
  mutate(LAD = elementnames,
         absdiff = TtestRESgreater %>% map_dbl(~.x$absdiff),
         Percdiff = TtestRESgreater %>% map_dbl(~.x$Percdiff))

#This is so cool, Also needs to be discussed in great detail, it is probablu due to the demolition and renovation of council housing
TtestRES2 %>% ggplot(.,aes(x= absdiff, y = Percdiff)) + geom_point() 
TtestRES2 %>% ggplot(.,aes(x= absdiff, y = p.value)) + geom_point()
TtestRES2 %>% ggplot(.,aes(x= Percdiff, y = p.value)) + geom_point()


#Perform ANOVA on the difference between the ratios of the groups on the bootrapped list
ANOVARES <- BootStrapRES %>% 
  map_df(~aov(.x$RatioExvsAct~.x$class) %>% tidy) %>% 
  filter(term != "Residuals") %>%
  select(-term) %>%
  mutate(LAD = elementnames)

WardData <- ls(pattern = "DATA") %>%
  map_df(~eval(parse(text=.x)) %>%
           select(WardLowUsePerc) %>%
        mutate( WardLowUsePerc = ifelse(is.na(WardLowUsePerc),0, WardLowUsePerc)) %>%
          summarise( maxPerc = max(WardLowUsePerc, na.rm=TRUE),
          minPerc = min(WardLowUsePerc, na.rm=TRUE),
          diffPerc = maxPerc-minPerc,
          LAD = sub("DATA", "", .x)))


skew <- BootStrapRES %>% map_df(~.x %>% group_by(class) %>%
  summarise(skew = mean(RatioExvsAct, na.rm = TRUE)) %>%
  summarise(skew = skewness(skew))
)


Combine1 <- left_join(ANOVARES, TtestRES2, by = "LAD" ) %>% left_join(WardData,by = "LAD" ) %>% bind_cols(skew)


test <- BootStrapRES$Ceredigion
#look at specific data
BootStrapRESA$Ceredigion %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")


```


Why are some areas with negative difference?

The max percentage of low use is 5%
There is the council estate renovation effect.
All the areas are Urban
Also check deprivation,

```{r}

Combine1 %>% ggplot(.,aes(x= maxPerc, y = abs(Percdiff))) + geom_point()

Combine1 %>% ggplot(.,aes(x= abs(maxPerc), y = p.value.y)) + geom_point()

#P.value is low if diff perc is over 5%
#Both southwark and Tower of london have concil flat renovation?
#Southwark the Aylesbury estate is being redeveloped making emptyness much higher than expected
#The blackwall an cubitt are being redevleoped with the blackwall reach, some housing is empty others are still occupied demolishin has not occured
Combine1 %>% ggplot(.,aes(x= diffPerc, y = p.value.y)) + geom_point()

Combine1 %>% ggplot(.,aes(x= maxPerc, y = p.value.y)) + geom_point() +
  labs(title = "Comparing tatistical Significance of LUPs being more expensive than RHs and the maximum concentration of LUPs in a ")

#Boring doesn't show anything interesting
Combine1 %>% ggplot(.,aes(x= p.value.x, y = p.value.y, colour =diffPerc>5 )) + geom_point()

Combine1 %>% ggplot(.,aes(x= maxPerc, y = p.value.y, colour =absdiff>0 )) + geom_point()

test <- Combine1 %>%
  select(LAD,p.value.x, p.value.y, absdiff , maxPerc, minPerc,diffPerc, skew)


Combine1 %>% ggplot(.,aes(x= skew, y= p.value.y)) + geom_point()

```



```{r}


test <- Combine1 %>% filter(p.value.y>0.05)
```

