---
title: "Untitled"
author: "Jonathan Bourne"
date: "5 July 2017"
output: html_document
---


Islington should be removed and put back in when they send the correct data, it is giving a false negative

#this uses rank for distance from LAD I think it should be dist check this

#ico complaint ref
fs-506-897-47

Should type B be included? or just type A?


What's the Deal with Westminster?
Westminsters Data is very low, I want to check what codes are going on.
Westminster
PCLB00: Second home class B/A
PCLB50: 
PCLC00: Empty and unfurnsished
PCLC99: 
PCLD00: Undergoing major repairs
PCLJ50:
Single:

#Setup

```{r setup}
setwd( "~/Dropbox/SSE/Empty Homes/EmptyHomesCode/SubCode")
source("Setup.R")

setwd(Functions)
list.files() %>% map(source)

Figures <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Empty Homes Write up/Figures"
source(file.path(CommonCode, "AuxdataLoad.R"))
```


#Cumbria
```{r}
setwd(file.path(RegionsComp, "Region North West"))

BarrowCUMBRIADATA <- read_excel("Barrow-in-FurnessExemptionsLSOA.xlsx", sheet=1)[1:4]%>%  
  StructureData(.,lowuse = c(2:6,8))

SLakelandCUMBRIADATA <- read_excel("South LakelandExemptionsLSOA.XLSX", sheet=1)[,1:4] %>%
    StructureData(., lowuse=2:9)

#only inlcudes postcodes so the mergeing needs to be done manually
CopelandCUMBRIADATA <- read_excel("CopelandFOI 5778 data 100517 CBC.XLSX", sheet=1) %>% 
  mutate(Postcode = sub(" ", "", Postcode)) %>%
  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=`Disc Type Ind`, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
  StructureData()


EdenCUMBRIADATA <- read_excel("EdenDiscountsLSOA.xlsx"  , sheet=1)[1:4] %>%  
  StructureData(.,lowuse = c(2:6,8))

CarliseCUMBRIADATA <- read_excel("FOI 5846 5983-CarlisleDiscountsLSOA June 2017.xlsx"  , sheet=1)[1:4] %>%  
  StructureData(.)

AllerdaleCUMBRIADATA <- read_excel("F17.132_Copy of Allerdale discounts LSOA_170815.xlsx"  , sheet=1)[1:4] %>%  
  StructureData(c(4:10))

```


#Manchester

```{r}
list.files()

OldhamMANCDATA <- read_excel("FOI 10635 OldhamDiscounts LSOA.xlsx", sheet = 1 )[c(1,4:6)] %>%  
  StructureData(., c(5:6,8:11))

ManchesterMANCDATA <- read_excel("ManchesterDiscountsLSOA.xlsx", sheet = 1 )[1:4] %>%  
  StructureData(. )

RochdaleMANCDATA <- read_excel("Rochdale Both.xlsx" , sheet = 1 )[1:4] %>%  
  StructureData(., c(5,6,14,15,20:22))

TamesideMANCDATA <- read_excel("Tameside FOI 6257A2.xlsx", sheet = 1 )[1:4] %>%  
  StructureData(. )

TraffordMANCDATA <- read_excel("Trafford Exemption and Levy.xlsx" , sheet = 1 )[1:4] %>%
  filter(Exemption_type =="LEVY") %>% 
  bind_rows(.,read_excel("TraffordDiscountsLSOA.XLSX", sheet = 1 )[1:4] %>% rename(Exemption_type = Class)) %>%
  StructureData()

WiganMANCDATA <- read_excel("Wigan 5528 DISCOUNTS.xlsx", sheet = 1 )[1:4] %>%  
  StructureData(., lowuse = c(2:3, 5:9) )


#hide plot
#ls(pattern = "MANC") %>% map_df(~eval(parse(text=.x))) %>% PlotMap(., AG)


```


#West Midlands Brum
```{r}

setwd(file.path(RegionsComp, "Region West Midlands"))

SandWellDATA <- read_excel("FOI - SandwellDiscountsLSOA - FS57000079 Disc.xlsx" )[1:4] %>%  
  StructureData(2:6)

WolverhamptonDATA <- read_excel("WolverhamptonDiscountsLSOA.XLSX"  )[1:4] %>%  
  StructureData(c(2:5,7))

WalsallDATA <- read_excel("WalsallDiscountsLSOA.XLSX" )[1:4] %>%  
  StructureData(c(4:5,7:8))



```


#SouthWest

##Cornwall

```{r}

setwd(file.path(RegionsComp, "Region South West"))

CornwallDATA <- read_excel("Cornwall.xlsx", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
  StructureData(lowuse = c(2,23:28))
```

##Devon

```{r}

NorthDevonDATA <- read_excel("North DevonDiscountsLSOA.XLSX", sheet=1)[1:4] %>%
  StructureData  

PlymouthDATA <- read_excel("PlymouthDiscountsLSOA.XLSX" , sheet=1)[1:4] %>%
  StructureData(lowuse = 4:8)

TorbayDATA <- read_excel("Torbay_discounts 1718551.xlsx"  , sheet=1)[1:4] %>%
  StructureData()

MidDevonDATA <- read_excel("MidDevon FOI04942Information 3.xlsx" , sheet=1)[1:4] %>%
  StructureData(c(7,10:11,20:22,26,28))

TorridgeDATA <- read_excel("FOI_TorridgeDiscountsLSOA.XLSX" , sheet=1)[1:4] %>%
  StructureData(c(4:5,7:10,13))

```

##Somerset

```{r}
NorthSomsertDATA <- read_excel("1501796 North SomersetDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
  StructureData(lowuse= 2:6)  

MendipDATA <- read_excel("Mendip 356 20170706 Response.xlsx" , sheet=1)[1:4] %>%
  StructureData(lowuse= c(37:39,52:54,65:66,69)) 

#Bristol appears to have not included second homes
#BristolDATA <- read_excel("Bristol%2c City ofDiscountsLSOA_as at 110817.xlsx")[c(1:4)] %>%
#  StructureData()

```


##Dorset

```{r}
PooleDATA <- read_excel("Copy of FOI - 265 - Bourne - PooleDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
  StructureData(lowuse = c(5,11:14,18))

ChristchurchDATA <- read_excel("Christchurch FOI17 - 0312 - Bourne - Ctax Discounts and Exemptions.xls",
                               sheet=1)[1:4] %>%
  StructureData(lowuse = c(6,12:17,20))

WeymouthDATA <-  read_excel("63687 Weymouth and PortlandDiscountsLSOA - 010817.xlsx"    ,
                               sheet=1)[1:4] %>%
  StructureData()

WestDorsetDATA <-  read_excel("47019 West DorsetDiscountsLSOA - 010817.xlsx"     ,
                               sheet=1)[1:4] %>%
  StructureData()



PurbeckDATA <-  read_excel("PurbeckDiscountsLSOA - 010817.xlsx"      ,
                               sheet=1)[1:4] %>%
  StructureData()

```


##Wiltshire

```{r}
#Wiltshire have not included everything
WiltshireDATA <- read_excel("Wiltshire ENQ07536 - Council tax discounts 2.xlsx",
                               sheet=1)[1:4] %>%
  StructureData(lowuse = 3:8)

SwindonDATA <- read_excel("Swindon - 7th July 2017 - Part 2 (Discounts).xlsx" ,
                               sheet=1)[1:4] %>%
  StructureData(2:6)
```

#East of England

##Suffolk


```{r}
setwd(file.path(RegionsComp, "Region East of England"))
list.files()


#Serparete in to the two LADS
# CoastWaveDATA <- bind_rows(read.xlsx("FOI IMT178324 SuffolkCoastal.xlsx")[1:4] , read.xlsx("FOI IMT178324 Waveney.xlsx")[1:4]) %>% setNames(make.names(names(.))) %>%
#   mutate(Exemption.type = Exemption.type %>% trimws %>%
#            make.names %>% 
#            gsub("\\.{2,}" , ".", .))  %>%
#   StructureData(., lowuse = c(5,6,13,14,16:18))

CoastSUFFDATA <- read.xlsx("FOI IMT178324 SuffolkCoastal.xlsx")[1:4] %>% setNames(make.names(names(.))) %>%
  mutate(Exemption.type = Exemption.type %>% trimws %>%
           make.names %>% 
           gsub("\\.{2,}" , ".", .))  %>%
  StructureData(.,c(5,6,11,12,14:16))

WaveneySUFFDATA <- read.xlsx("FOI IMT178324 Waveney.xlsx")[1:4] %>% setNames(make.names(names(.))) %>%
  mutate(Exemption.type = Exemption.type %>% trimws %>%
           make.names %>% 
           gsub("\\.{2,}" , ".", .))  %>%
  StructureData(., lowuse = c(5,6,13,14,16:18))

StEdmundsDATA <- read.xlsx("se FOI 146  3948502_Copy+of+St+EdmundsburyDiscountsLSOA.xlsx")[1:4] %>%
  StructureData()

ForestHeathDATA <- read.xlsx("FH FOI 146 Discounts.xlsx")[1:4] %>%
  StructureData()

IpswichDATA <- read_xlsx("IpswichDiscountsLSOA.xlsx")[1:4] %>%
   StructureData(c(2:4,6:11,13:15))

#Mid Suffolk and Babergh
#These have been combined and are just the postcodes so need to be fixed
#Missing loads of postcodes
MidSuffolkDATA <- read_excel("MidSuffolk FOI MF379 1718 Discount.xlsx") %>%
mutate(Postcode = gsub(" ", "", `Post Code`)) %>%
 left_join(.,PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=`Discount Type Description`, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code, Admin_district_code) %>%
  StructureData(c(2:12,14:15))


BaberghDATA <- read_excel("Babergh FOI BF378 1718 Discount.xlsx")%>%
mutate(Postcode = gsub(" ", "", `Post Code`)) %>%
 left_join(.,PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=`Discount Type Description`, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code, Admin_district_code) %>%
  StructureData(c(2:6,8:11,13:15))


```

##Norfolk
```{r}
#Broadlands is unsuable, due to lack of data collection.
#This is being checked
BroadlandsDATA <- read_excel("BroadlandDiscountsLSOA.xlsx", sheet=1)[1:4] %>%
  StructureData(4:9)

KingsLynnDATA <- read_excel("197782 - King s Lynn and West NorfolkDiscountsLSOA (2).xlsx" , sheet=1)[1:4] %>%
  StructureData(2:11)

NorthNorfolkDATA <- read_excel("North NorfolkDiscountsLSOA.XLSX" , sheet=1)[1:4] %>%
  StructureData()

BrecklandsDATA <- read_excel("BFOI-003031 BrecklandDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
  StructureData()

#they deleted the classes
SNorfolkDATA <- read_excel("SNorfolk 17-307 Discounts.xlsx"  , sheet=1)[1:4] %>%
  StructureData()

```


##Cambridge
```{r}
EastCambsDATA <- read_excel("EC FOI 130 - DISC_FOI_0_3944413b.xlsx", sheet=1)[1:4] %>%
  StructureData()


FenlandDATA <- read_excel("FL FOI 4544 DISCOUNTS.XLSX" , sheet=1)[1:4] %>%
  StructureData()

HuntingdonDATA <- read_excel("Huntingdonshire  FOI 568discounts.xlsx" , sheet=1)[1:4] %>%
  StructureData(lowuse = 2:8)

PeterboroughDATA <- read_excel("Peterborough 1707267585 completed.xlsx" , sheet=1)[1:4] %>%
  StructureData(lowuse = c(4,6:7,11))

CambridgeDATA <- read_excel("566 - Copy of Copy of CambridgeDiscountsLSOA .xlsx" , sheet=1)[1:4] %>%
  StructureData(2:5)

```

#Brightong and Hove


```{r}

setwd(file.path(RegionsComp, "Region South East"))
list.files()

BrightonDATA <- read_excel("Copy of Brighton and HoveDiscountsLSOA (4).xlsx", sheet=1)%>% .[,c(2,3:5)] %>%
  StructureData(lowuse = 2:8)
#MakeLeaflet(BournemouthDATA)

```


#Yorkshire and the Humber
```{r}
setwd(file.path(RegionsComp, "Region Yorkshire and The Humber"))

#Hull

HullDATA <-read_excel("KINGSTON UPON HULL%2c CITY OFDISCOUNTSLSOA.XLSX")[-c(c(1:6)),1:4] %>%
  StructureData(.)

#Harrowgate

HarrogateDATA <-read_excel("Harrogate DiscountsExemptionsLSOA.xlsx" )[,1:4] %>%
  StructureData(.,3:10)

#Selby
SelbyDATA <-read_excel("SelbyExemptionsLSOA.xlsx" )[,1:4]%>%
  StructureData(20:27)


# HambletonDATA <- read_excel("HDC1088.xlsx")[,1:4] %>%
#  StructureData()

ScarboroughDATA <- read_excel("FOIA 5156 Scarborough Discounts LSOA.xlsx"  )[,1:4]%>%
  StructureData(2:8)



# Middlesbrough sent the wrong data
# MiddlesbroughDATA <- read_excel( "Middlesbrough FOI RES - 011397 Discounts.xlsx"   )[,1:4]%>%
#   StructureData()

#Ryedale
RyedaleDATA <-  read_excel("Ryedale FOI 4597.xlsx")[,1:4]%>%
  StructureData(2:6)

#Crave they sent full addresses by mistake I'll do a temporary fix
CravenDATA <- read_excel("Craven Discounts.xlsx" ) %>%
  setNames(make.names(names(.))) %>%
  mutate(Postcode = str_split(Full.Property.Address, "(,)(?!.*,)", simplify = T)[,2] %>% 
           gsub(" ", "", .)) %>%
  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=Discount.Type.Description, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
  StructureData(c(2:5,7))

#Redcar and cleveland

RedcarDATA <-  read_excel("Redcar 0614 attachment 1.xlsx")[,1:4]%>%
  StructureData(2:10)


CalderdaleDATA <- read_excel("Copy of CalderdaleDiscountsLSOA.xlsx" )[,1:4]%>%
  StructureData(c(7,10,22:25))

BradfordDATA <- read_excel("Copy of BradfordDiscountsLSOA.xlsx")[1:4] %>%
  StructureData(c(2:7))


RichmondshireDATA <- read_excel("Richmondshire FOI 4960.xls", col_names = FALSE)[1:2] %>%
    setNames(c("Exemption.type", "Postcode")) %>%
  mutate(Postcode = sub(" ", "", Postcode)) %>%
  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
  StructureData(lowuse = c(2:7))
  

KirkleesDATA <- read_excel("Jonathan Bourne KirkleesDiscountsLSOA Complete.xlsx" )[1:4] %>%
  StructureData(2:5)

```

#North East

##Tyneside

```{r}

setwd(file.path(RegionsComp, "Region North East"))
list.files()
#Not sure all are there ask for confirmation
 SunderlandDATA <- read_excel("Sunderland Freedom of Informaton Request from Jonathan Bourne- 17-07-21-Discounts.xlsx"  , sheet=1)%>% .[,1:4] %>%
   StructureData(lowuse = c(2:4,6,8:10))


NewcastleDATA <- read_excel("Newcastle upon TyneDiscountsLSOA.xlsx", sheet=1)%>% .[,c(1,3:5)] %>%
    StructureData(lowuse = 2:7)


#FOr some reason Gateshead has the wrong LAD11CD I don't know why. I have changed it to the right one but feel that perhaps I should check them all, but how?
GatesheadDATA <- read_excel("Copy of GatesheadExemptionsLSOA.XLSX"   , sheet=1)%>% .[,1:4] %>%
   StructureData(lowuse = c(2:3, 20,22:25)) %>%
  mutate(LAD11CD = ifelse(is.na(LAD11CD), NA, "E08000037"))

STynesideDATA <- read_excel("FOI 17.18456 - South Tyneside Discounts.xlsx", sheet=1)[,c(1,4:6)] %>%
    StructureData(c(32:35,38))

```


##Northumberland

```{r}
NorthumberlandDATA <- read_excel("FOI 2762 data NorthumberlandDiscounts.xlsx", sheet=1)%>% .[,1:4] %>%
    StructureData(2:7) %>%
  #The LAD code is wrong for some reason
  mutate(LAD11CD = "E06000057")

```


##Durham
```{r}
  
DurhamDATA <- read_excel("County DurhamDiscountsLSOA.XLSX" , sheet=1) %>% .[,c(1,4:6)] %>%
    StructureData()

  DarlingtonDATA <- read_excel("Darlington DBC-0809-17.xlsx" , sheet=1) %>% .[,1:4] %>%
    StructureData()

  HartlepoolDATA <- read_csv("FOI 7942 HartlepoolDiscountsLSOA.csv") %>% .[,1:4] %>%
    StructureData(2:7)
  

```


#Wales

```{r}

setwd(file.path(RegionsComp, "Region Wales"))
list.files()

#Ceredigion completed some major Student Halls which were transferred to the University, this created some very large B type transfers which artificially push the cost of second homes lower than the price of regular homes.

CeredigionDATA <- read_excel("CTAX - Ceredigion Discounts LSOA.xlsx", sheet=1)%>% .[,1:4] %>%
  StructureData(lowuse =c(8:13,15))

MonmouthDATA <- read_excel("MCC Discounts Jul 17.xlsx", sheet=1)%>% .[,1:4] %>%
  StructureData(lowuse = c(4:8))


#includes the zero class which is descibeed as 
#ZERO – tis is a 50% reduction which applies after exemptions that are time limited, have expired. They are awarded on the basis that the property remains unoccupied and unfurnished.
  CarmarthenDATA <- read_excel("CarmarthenshireDiscountsLSOA.XLSX" , sheet=1)%>% .[,1:4] %>%
    StructureData()

#Strangely low numbers checking
# PowysDATA <- read_excel("PowysDiscountsLSOA.XLSX"    , sheet=1)%>% .[,1:4] %>%
#   StructureData(lowuse = c(3,5:6))

#It seems Conwy really is this short on the discounts  
ConwyDATA <- read_excel("Conwy FOI 0260-17.xlsx" , sheet=1) %>%
  rename(Postcode = geo_postcode) %>%
  mutate(Postcode = sub(" ", "", Postcode)) %>%
  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=disc_type_desc, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
  StructureData(lowuse = c(2,4))

DenbigshireDATA <- read_excel("FOI 2503 Denbighshirev2 .xlsx" , sheet=1)%>% .[,1:4] %>%
    StructureData(c(8:9,11,13))

WrexhamDATA <- read_csv("WrexhamDiscountsLSOA.csv" )%>% .[,1:4] %>%
    StructureData(2:5)

#Pembrokeshire didn't send all the data
PembrokeshireDATA <- read_excel("Copy of PembrokeshireDiscountsLSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
    StructureData(3)

FlintshireDATA <- read_excel("FOI R014329 FlintshireDiscounts LSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
    StructureData()


```


# London using the full data

```{r}
#Source the code from another file as it is very long
source(file.path(CommonCode, "LondonFullProcesss.R"))

#MakeLeaflet(NewhamLONDATA)

```

#Semi data 

The LSOA will be assigned empty and low use homes by percentage

```{r}
#ward folder
setwd(SemiLondon)


wardnames <- EW2 %>% group_by(Admin_ward_code, WD16NM) %>% summarise(counts = n(), LAD11NM = first(LAD11NM), LAD11CD = first(LAD11CD)) %>% arrange(WD16NM)


#Wandsworth

WandsworthLONDDATA <- read_excel("wandsworth2.xlsx",  skip = 3 ) %>% select(1,3) %>% 
  group_by(`Ptc Wardname`) %>% summarise(Empty = sum(`Count Current Occupancy Discounts`)) %>% ungroup %>% 
  arrange(`Ptc Wardname`) %>% 
  filter(!is.na(`Ptc Wardname`)) %>% 
  bind_cols(., wardnames %>% filter(LAD11NM == "Wandsworth") %>% 
              select(Admin_ward_code)) %>%
  mutate(LowUse = Empty) %>%
  SemiDataStructure


#Merton

MertonLONDATA <- read_excel("merton1.xlsx" )[,-2] %>%setNames(make.names(names(.))) %>% slice(-1) %>% arrange(X__1) %>%
  filter(X__1 != "Norbury", X__1!="Nightingale", X__1 !="Stonecot") %>% 
    bind_cols(., wardnames %>% filter(LAD11NM == "Merton") %>% 
              select(Admin_ward_code)) %>%
  mutate(Empty =   Disc.Class.C.Vacant.dwelling + Disc.class.C.Long.term.empty + Premium.Levy, LowUse =  Disc.Class.A.Second.home + Disc.Class.B.second.home ) %>%
  SemiDataStructure

#Kingston

KingstonLONDATA <- read_excel("Kingston1.xlsx"  )%>% setNames(make.names(names(.))) %>%
  arrange(X__1) %>% slice(1:16) %>%
  bind_cols(., wardnames %>% filter(LAD11NM == "Kingston upon Thames") %>% 
              select(Admin_ward_code)) %>%
  mutate(Empty = Empty...Furnished..0.. + Empty.Homes.Premium + LONG.TERM.EMPTY..0.. + Structural.Repair..0.., LowUse = Empty + X2nd.Home..0..) %>%
  SemiDataStructure


#TowerHamlets
TowerLONDATA <- read_excel("Towerhamlets.xlsx")[,c(1,3)] %>% 
  filter(!is.na(DiscClass)) %>%
  group_by(Ward, DiscClass) %>%
  summarise(count = n()) %>% ungroup %>%
  spread(., key =DiscClass, value = count, fill = 0 ) %>% 
  mutate(Empty = rowSums(.[,4:8]), LowUse = B+BE+Empty) %>% 
  slice(c(1:13, 15:17, 14, 18:20)) %>%
   bind_cols(., wardnames %>% filter(grepl("Tower", LAD11NM))) %>%
  SemiDataStructure


HaveringLONDATA <- read_excel("AIR12965P Informatiion provided by Council Tax.xlsx" ) %>%
  rename(DiscClass = X__1) %>%
  select(-Mawneys, -`Aveley & Uplands`, -Whalebone) %>%
  gather(key = "ward", value = "counts", -DiscClass) %>%
  spread(key= DiscClass, value = counts, fill = 0) %>%
  mutate(Empty = rowSums(.[,c(5:6,14,17)]), LowUse = Empty+ `Second Home Class A`+ `Second Homes Class B`) %>% 
  bind_cols(., wardnames %>% filter(grepl("Havering", LAD11NM))) %>%
  SemiDataStructure

```

General Stats
#UK population


```{r}

#number of LUPS and Total Homes
DataCover <- ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x))) %>% 
  filter(!is.na(LAD11NM)) %>%
  summarise(
           TotalLADs = length(ls(pattern = "DATA", envir = globalenv())), #bits of other LADS cause the number to be higher than reality so the ls function is used again
           PercLADs = length(ls(pattern = "DATA", envir = globalenv()))/(EW2$LAD11NM %>% unique %>% length()),
           LowUse = sum(LowUse, na.rm = T),
           Homes = sum(Homes, na.rm = T),
           PercHomes = Homes/sum(EW2$Homes),
           Population = sum(Pop, na.rm= T),
           PercPop = Population/sum(EW2$Pop)) %>%
  mutate_if(.<1, funs(signif(.,3))) %>%
  mutate_if(.>1, as.integer) %>%
  mutate_all(as.character) %>% 
  gather

DataCover 

xtable(DataCover, caption="Summary of collected data coverage",
       label = "tab:DataCover") %>% 
  print(., type="latex", file=file.path(TexTables,"DataCover.tex"))

#Percentage of EW LADS
length(ls(pattern = "DATA"))/(EW2$LAD11NM %>% unique %>% length())

#check which lads are present even though I don't have data due to postcode matching
#test <- ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x)))  %>% arrange(LAD11NM)
#unique(test$LAD11NM)

```


#Plot stuff
```{r}
x <-bind_rows(SouthwarkLONDATA, TowerDATA, LambethLONDATA, CoLLONDATA, NewhamLONDATA) %>% MakeLeaflet

z<- MakeLeaflet(AllerdaleDATA)
z
# 
setwd(basewd)
 saveWidget(z, file=file.path(basewd, "Cumbria.html"), selfcontained = TRUE )

#testSouth <- DistribCompareBootstrapper(SouthwarkLONDAls(pattern = "DATA")TA, 1652, 1000)
testSouth %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100) %>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

ValueTtest(test)

PlotMap(BexleyLONDATA)

z <-ChelseaLONDATA %>% 
  mutate(LAD11CD = ifelse(LAD11CD  == "E09000005", "E05009388" ,LAD11CD)) %>% #kept adding in Barnet
  filter(LAD11NM =="Kensington and Chelsea") %>% 
  MakeLeaflet()

mapshot(z, file = file.path(Figures, "Chelsea.pdf"))

CumbriaPlot <- ls(pattern = "CUMBRIA") %>% 
  map_df(~get(.x)) %>%
   group_by(LSOA_CODE) %>%
   summarise(LowUse = sum(LowUse, na.rm = TRUE)) %>% 
  CalcLowUse()

z<- MakeLeaflet(CumbriaPlot)

mapshot(z, file = file.path(Figures, "Cumbria.pdf"))



z<- MakeLeaflet(CornwallDATA)
mapshot(z, file = file.path(Figures, "Cornwall.pdf"))

z<- MakeLeaflet(BarrowCUMBRIADATA)
mapshot(z, file = file.path(Figures, "Barrow.pdf"))

```

#Look at saleries
```{r}

unafford <- ls(pattern = "DATA") %>%
  map_df(~get(.x) %>% select(LowUse:WardLowuseClass)) %>%
  group_by(MSOA11CD) %>%
  summarise(LowUse = sum(LowUse, na.rm = T),
            Homes = sum(Homes, na.rm = T),
            Pop = sum(Pop, na.rm = T)) %>%
  mutate(LowUsePerc = LowUse/Homes) %>%
  left_join(IncomeEst, by = "MSOA11CD") %>%
  mutate(decile = ntile(ratio, 20))


unaffordExLon <- unafford %>%
  filter(Region.name != "London") %>%
  mutate(decile = ntile(ratio, 50))

#London follows the same pattern it just happens further up the scale
unaffordLon <- unafford %>%
  filter(Region.name == "London") %>%
  mutate(decile = ntile(ratio, 50))

cor(unaffordExLon$LowUsePerc, unaffordExLon$ratio)
cor(unafford$Yearly.income, unafford$ratio, "complete.obs")

cor(unaffordExLon$LowUsePerc, unaffordExLon$MedianPrice)
cor(unaffordExLon$Yearly.income, unaffordExLon$MedianPrice)
cor(unafford$Yearly.income, unafford$MeanPrice, "complete.obs")


test <- lm(MedianPrice ~ LowUsePerc + Yearly.income, data  = unafford)

summary(test)

decile <- bind_rows(mutate(unaffordExLon, type = "Excluding London"), 
                    mutate(unafford, type = "Including London"),
                    mutate(unaffordLon, type = "Only London")) %>%
    group_by(type) %>%
    mutate(decile = ntile(ratio, 50)) %>%
      group_by(decile, type) %>%
    summarise(mean = mean(LowUsePerc),
              median = median(LowUsePerc),
              counts = n()
              ) 

#Looking at the relationship between unaffordability and LUP percentage

decile %>% ggplot(aes(x= decile, y = median)) + 
  facet_grid(.~type) + 
  #geom_point(data =unaffordExLon , aes(x= decile, y = LowUsePerc), alpha = 0.2 )+
  geom_point(aes(colour = type))  +
  labs(x = "ith 2 percentile group", y = "median Percent Low Use") + 
  theme(legend.position= "none") + 
  geom_smooth(method="loess",se=FALSE, colour = "black")
SaveFig("LowUsePercVSratio.pdf")

unafford %>%
  ggplot(aes(x= ratio, y = MeanPrice)) + geom_point()

#Example of the theoretical relationship

data_frame(Index = 1:100) %>%
  mutate(Primary = exp(-0.05*(Index))+0.05, 
         Auxilary = (exp(Index/100)-1),
    Total = Primary + Auxilary) %>%
  gather(key = "Type", value = "value", -Index) %>%
  ggplot(aes(x= Index, y = value, colour = Type )) +
  geom_point() +
  labs(title = "LUP percentage as a function of primary and Auxilary demand",
       x = "Demand",
       y = "LUP percentage") +
  theme(
  axis.text.x = element_blank(),
  axis.text.y = element_blank()
  )
SaveFig("TheoreticalDemand.pdf")


unaffordLAD <- unafford %>%
  rename(LAD11CD = Local.authority.code) %>%
  group_by(LAD11CD) %>%
  mutate(TotInc = Yearly.income*Pop) %>%
  summarise(TotInc = sum(TotInc),
            Pop = sum(Pop)) %>%
  mutate(meanInc = TotInc/Pop)

```


#Bootstrap

Now all the data is loaded each LAD needs to be bootstrapped

```{r}

setwd(basewd)

BootStrapRESExO <-LoadAddDistribCompare("BootStrapRESExO.rds", 
                                         PropertyTypes = c("D", "S", "T", "F"))

elementnames<- names(BootStrapRESExO)

#Used when elements need to be deleted and reloaded
#saveRDS(BootStrapRESExO, "BootStrapRESExO.rds")

#Make a summary dataframe
Combine1ExO <- BootResSummaryData(BootStrapRESExO) 
```


#Analyse Boostrap


```{r}
test <- BootStrapRESExO$WestminsterLON%>% 
  group_by(class) %>%
  summarise_all(funs(mean))


test2 <- test %>%
  select(-class) %>%
  summarise_all(funs(sum)) %>%
  mutate(LowUseValue = LowUseValue/1e9)


#99% of the LADs are significantly different from 0 at the 95% level
sum(Combine1ExO$Ttest.p.value>0.975 |Combine1ExO$Ttest.p.value<0.025)/nrow(Combine1ExO)

PlotClassDiff(BootStrapRESExO$ChelseaLON, "Kensington and Chelsea")
SaveFig("ClassdiffChelsea.pdf")

PlotClassDiff(BootStrapRESExO$Cornwall, "Cornwall")
SaveFig("ClassdiffCornwall.pdf")

PlotClassDiff(BootStrapRESExO$BarrowCUMBRIA, "Barrow")
SaveFig("ClassdiffBarrow.pdf")

test <- BootStrapRESExO %>% 
  bind_rows %>%
  group_by(class, ID) %>%
  summarise_all(sum) %>%
  ungroup %>%
  mutate(HomesPrice = HomesValue/Homes,
         LowUsePrice = LowUseValue/LowUse,         
         ratio = LowUse/Homes,
         HomesPerc = Homes/sum(Homes, rm.na = T),
         LowUsePerc = LowUse/sum(LowUse, rm.na = T),
         ClassPerc = LowUse/Homes,
         ExpectedHomes = HomesPerc*sum(LowUse, rm.na = T),
         RatioExvsAct = LowUse/ExpectedHomes
         ) %>%
        mutate(class = fct_relevel(class,c("Lower", "Mid", "Upper", "Prime", "Super")) )

test2 <- test %>% group_by(class) %>%
  summarise_all(mean)

PlotClassDiff(test)
SaveFig("ClassdiffAllData.pdf")


test %>% 
  mutate(RatioExvsAct = LowUsePrice/HomesPrice) %>%
   mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
     ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + 
     geom_boxplot() + 
     labs(title = "Observed within class difference in Price from expected for LUPs", 
          y = "% difference from expected")
SaveFig("PricediffAllData.pdf")


```



#Explore results

```{r}

LADNMs <- EW2 %>% group_by(LAD11CD) %>%
  summarise(LAD11NM = first(LAD11NM))

PropertyTypes <- c("D", "S", "T", "F")

#calulcate the number of properties sold and the mean price
ABratio <- prices %>% 
  filter(X5 %in% PropertyTypes) %>%
  group_by(Admin_district_code, X15) %>%
  summarise(count = n(), 
            mean = mean(X2)) %>%
  rename(LAD11CD = Admin_district_code)

ABratio2 <- ABratio%>%
  select(-mean) %>%
spread(key = X15, value = count) %>%
  mutate(Countratio = B/(A+B)) %>%
  rename(CountofA = A, CountofB = B)

ABratio3 <- ABratio%>%
  select(-count) %>%
spread(key = X15, value = mean) %>%
  mutate(Valueratio = B/(A)) %>%
  rename(MeanofA= A, MeanofB = B)


CombineAB <-left_join(ABratio2, ABratio3, by = "LAD11CD") %>%
  left_join(Combine1ExO, ., by = "LAD11CD") 

rm(ABratio); rm(ABratio2); rm(ABratio3)


CombineAB %>%
  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Valuerat HounslowLONDATA <- read_excel("Hounslow Discounts - Bourne Info -210817.xls" )io>1)) + geom_point()

```


#Inlcuding deprivation
```{r}

#creating the empty deprivation extent
maxLSOA <- max(LSOADep$Rank..where.1.is.most.deprived.)

ExtentWeight <- LSOADep%>%
  mutate(percentile = (Rank..where.1.is.most.deprived./maxLSOA),
         perc2 = percentile-0.11,
         weight = ifelse(percentile<.11|percentile>.3,0, 0.95 - (0.95/.20)*perc2 ),
         weight = ifelse(percentile<0.11, 1, weight)) %>%
  select(LSOA_CODE, weight)

#Create the extent of deprivation of the LUPs
LUPdepExt <- ls(pattern = "DATA") %>% map_dbl(~{
df <- get(.x)
test <- df %>% 
  left_join(., ExtentWeight, by= "LSOA_CODE")  %>%
  mutate(WeightedLUP = (LowUse*weight)/sum(LowUse))

sum(test$WeightedLUP, na.rm = TRUE)
})


#Add in deprivation
Combine1ExO <- select(LADDep, LAD11CD ,Extent) %>% 
  left_join(CombineAB, ., by = "LAD11CD") %>%
  mutate(LUPdepExt) 


Combine1ExO %>% ggplot(.,aes(x= maxPerc, y = LUPdepExt, colour = absdiff>0)) +
  geom_jitter()

Combine1ExO %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = LUPdepExt>0.10)) +
  geom_jitter()

```

Rural Urban split
```{r}
setwd(DataFolder)

Rural <- read_csv( "RUC11_LAD11_ENv2.csv" )[-1,] %>%
  setNames(make.names(names(.))) %>%
  rename(PercRural = Rural.including.hub.towns..rural...rural.related..population1_1) %>%
  select(LAD11CD, PercRural) %>%
  mutate(PercRural = as.numeric(PercRural))

#Update Gateshead and Northumberland Codes
Rural$LAD11CD[Rural$LAD11CD == "E08000020"] <-"E08000037"
Rural$LAD11CD[Rural$LAD11CD == "E06000048"] <- "E06000057"

Combine1ExO <- Combine1ExO %>%
  left_join(Rural, by = "LAD11CD")

```


#Model

```{r}
LADprice <- prices %>%
  filter(X5!= "O") %>%
  group_by(Admin_district_code) %>%
summarise(price = mean(X2)) %>%
  mutate(pricepercent = percent_rank(price))

ModelMe <- Combine1ExO %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
  left_join(Vacants, by = "LAD11CD") %>%
  mutate(VacantsPerc = Vacants/Homes,
         LTVPerc = Vacants/Homes) %>%
  #filter out wales
  filter(!grepl("W", LAD11CD)) %>%
#  select(LAD, absdiff, LUPdepExt,  maxPerc,Ttest.p.value, pricepercent) %>%
  left_join(Rural, by = "LAD11CD") %>%
  mutate(Reference = as.factor(absdiff>0) ) %>%
  #scaled so that the binomial can be interpreted
  mutate(pricepercent = scale(pricepercent),
         LUPdepExt = scale(LUPdepExt),
         maxPerc = scale(maxPerc))

#This uses the local mean so that has to be run first before the code works
# ModelMe <- Combine1ExO2 %>%
#   left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
#   #filter out wales
#   filter(!grepl("W", LAD11CD))%>%
#   select(LAD11NM, absdiff, LUPdepExt, Extent, maxPerc,Ttest.p.value,  LAD11CD) %>%
#   mutate(outcome = LUPdepExt>Extent)  %>% 
#   left_join(LocalMean, by = "LAD11CD") %>%
#   left_join(LADprice, by = c("LAD11CD"="Admin_district_code")) %>%
#   mutate(priceRatio = (price/LocalMean)) %>%
#   mutate(LUPdepExt.Extent = LUPdepExt-Extent, price.LocalMean = price-LocalMean ) %>%
#   #make the Reference column properly
#   mutate(Reference = as.factor(absdiff>0) ) %>%
#   #scaled so that the binomial can be interpreted
#   mutate(pricepercent = scale(pricepercent),
#          LUPdepExt = scale(LUPdepExt),
#          maxPerc = scale(maxPerc),
#          priceRatio = scale(priceRatio))



ModelMe %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = outcome)) +
  geom_jitter()

rowsum(.)>5 ~TRUE
#classification

#LUPdepExt and Pricepercent are the only useful ones really
Binom <- glm(Reference~ LUPdepExt +LADPerc +maxPerc+ mean.y, family=binomial(link='logit'),data=ModelMe)

Binom <- glm(Reference~ Extent + price + VacantsPerc, family=binomial(link='logit'),data=ModelMe)

confusionMatrix(predict(Binom, ModelMe, type = "response")>0.5 , ModelMe$Reference)

test <- lm(Percdiff ~ LUPdepExt +LADPerc +maxPerc+ mean.y, data = ModelMe)

summary(test)


summary(Binom) 

coef(Binom) %>% as.data.frame
```

##perform many mode resamples and plot the results

```{r}



#binom

set.seed(1983)
ModelStats <- 1:1000 %>% map_df(~{
  TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))

  model <- glm(Reference~ LUPdepExt + price + VacantsPerc, 
               family=binomial(link='logit'),
               as.data.frame(TestResample$train))

  Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "response")>0.5,
                              as.data.frame(TestResample$test)$Reference) 

  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
          Confmat$byClass %>% as.matrix %>%t %>% data.frame,
          coefficients(model)%>% as.matrix %>%t %>% data.frame) %>%
  mutate(ID = .x)

}
)


ModelStats %>% ggplot(., aes(x= Accuracy)) +geom_density()

ModelStats %>%
  mutate(diff = Accuracy - AccuracyNull) %>% 
  ggplot(., aes(x= diff)) +geom_density()

ModelStats %>% ggplot(., aes(x= AccuracyPValue)) +geom_density()
ModelStats %>% ggplot(., aes(x= Kappa)) +geom_density()

t.test(ModelStats$Accuracy, ModelStats$AccuracyNull, alternative = "greater")


test <- ModelStats %>% 
  select( X.Intercept., LUPdepExt, maxPerc, pricepercent) %>%
  gather 

test %>% ggplot(.,aes(x = key, y = value, fill = key)) + geom_boxplot() + 
  labs(title = "Direction each variable pushes the outcome")

test %>% ggplot(.,aes(x = value, fill = key)) + geom_density( alpha = 0.5)


```



```{r}
set.seed(1983)
ModelStats2 <- 1:1000 %>% map_df(~{
  TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))

  model <- glm(Reference~ Extent + price + VacantsPerc, 
               family=binomial(link='logit'),
               as.data.frame(TestResample$train))

  Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "response")>0.5,
                              as.data.frame(TestResample$test)$Reference) 

  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
          Confmat$byClass %>% as.matrix %>%t %>% data.frame,
          coefficients(model)%>% as.matrix %>%t %>% data.frame) %>%
  mutate(ID = .x)

}
)



set.seed(1983)
ModelStats3 <- 1:1000 %>% map_df(~{
  TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))

  model <- glm(Reference~ LUPdepExt + price + VacantsPerc, 
               family=binomial(link='logit'),
               as.data.frame(TestResample$train))

  Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "response")>0.5,
                              as.data.frame(TestResample$test)$Reference) 

  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
          Confmat$byClass %>% as.matrix %>%t %>% data.frame,
          coefficients(model)%>% as.matrix %>%t %>% data.frame) %>%
  mutate(ID = .x)

}
)

Outcome <- bind_rows(data_frame(model = "generic", Accuracy = ModelStats2$Accuracy), 
data_frame(model = "cutsom", Accuracy = ModelStats3$Accuracy) )

Outcome %>%
  ggplot(.,aes(x = Accuracy, fill = model)) + geom_density(alpha = 0.3)


#The model that uses easily available data is 3% less accurate than the other model.
t.test(ModelStats2$Accuracy, ModelStats3$Accuracy)

cor(ModelMe$Vacants, ModelMe$VacantsPerc)

cor(ModelMe$Vacants, ModelMe$LTV)
cor(ModelMe$VacantsPerc, ModelMe$LTVPerc)

```



interpreting the coefficients of the model shows us that there is a natural tendency for LUPs to be more expensive than regular housing, the probability of them being more expensive increases if the local authority is already expensive compared to the rest of the local authorities. In addition the greater the maximum concentration of LUPs also increase the probability of them being more expensive than regular housing. However if the LUPs are generally in deprived areas then the probability of them being more expensive than regular housing decreases.

Using the models produced in the previous section I can now predict areas where primary purchases are being out competed across the England

```{r}

#Linear
set.seed(1983)
MultiCheckL <- 1:21 %>% map(~{
  TestResample <- resample_bootstrap(ModelMe)

  model <- glm(Reference~ Extent + price + VacantsPerc, 
               family=binomial(link='logit'),
               as.data.frame(TestResample))

  data_frame(x = predict(model, ModelMe, type = "response")>0.5) %>%
    setNames(paste("Model", .x, sep="_"))
}
) %>% bind_cols() %>% mutate(
  Outcome = case_when(
  rowSums(.)>ncol(.)/2 ~TRUE,
  rowSums(.)<=ncol(.)/2 ~FALSE
))

#Tree
set.seed(1983)
MultiCheck <- 1:111 %>% map(~{
  TestResample <- resample_bootstrap(ModelMe)

  model <- rpart(Reference~ Extent + 
                   price + 
                   VacantsPerc  
                 ,data=as.data.frame(TestResample))

  data_frame(x = predict(model, ModelMe, type = "prob")[,2]>0.5) %>%
    setNames(paste("Model", .x, sep="_"))
}
) %>% bind_cols() %>% 
  mutate(
  Outcome = case_when(
  rowSums(.)>ncol(.)/2 ~TRUE,
  rowSums(.)<=ncol(.)/2 ~FALSE
))

test <- ModelMe %>%
  bind_cols(., select(MultiCheck, Outcome)) %>%
  mutate(Correct = Reference == Outcome) %>%
  filter(!Correct) %>%
  select(LAD, Reference, Outcome)

confusionMatrix(MultiCheckL$Outcome, ModelMe$Reference)  
confusionMatrix(MultiCheck$Outcome, ModelMe$Reference)


ModelMe %>% 
  mutate(Outcome = as.logical(MultiCheck$Outcome)) %>%
  filter(Outcome != Reference) %>%
  select(LAD, Outcome, Reference)
  

LadHomes <-  EW2 %>%
  group_by(LAD11CD) %>%
  summarise(Homes = sum(Homes, na.rm = TRUE),
            Pop = sum(Pop, na.rm = TRUE))

tol <- 0

#random forest appears better than multilinear but when checked on many resamples it is worse... how? To much noise?
EnglandComp <- LADDep %>% 
  select (LAD11CD, LAD11NM = Local.Authority.District.name..2013., Extent)%>% 
  left_join(., Vacants, by = "LAD11CD") %>%
  left_join(LADprice, by = c("LAD11CD" = "Admin_district_code")) %>%
  left_join( LadHomes, by = "LAD11CD") %>%
  #left_join(Rural, by = "LAD11CD") %>%
  mutate(VacantsPerc = Vacants/Homes) 

#Preds <- predict(BinomExtent, EnglandComp , type = "response")
set.seed(1983)
Preds <- 1:111 %>% map(~{
  TestResample <- resample_bootstrap(ModelMe)

  model <- rpart(Reference~ Extent + price + VacantsPerc,data=as.data.frame(TestResample))

  data_frame(x = predict(model, EnglandComp, type = "prob")[,2]>0.5) %>%
    setNames(paste("Model", .x, sep="_"))
}
) %>% bind_cols() %>% 
  mutate(
  Outcome = rowSums(.)/ncol(.))

EnglandComp <- EnglandComp%>% 
  left_join(select(ModelMe, LAD11CD, Reference), by = "LAD11CD") %>%
  mutate(
    Significant.Competition = ifelse(is.na(Reference),
                                     unlist(Preds$Outcome), 
                                     as.logical(Reference))
    ) %>%
  mutate(

      Comp.Type = case_when(
      .$Significant.Competition<0.5-tol ~"No",
      .$Significant.Competition>0.5 + tol ~"Yes",
      .$Significant.Competition>0.5-tol & .$Significant.Competition<0.5+tol ~"Borderline"
      )
  ) %>%
  select(-Reference)



EnglandComp %>%
  ggplot(aes(x = Comp.Type, y= price, fill = Comp.Type)) + geom_boxplot()


#Estimated

EnglandCompTab <- EnglandComp %>%
  group_by(Comp.Type) %>%
  summarise(mean = mean(price),
            median = median(price),
            Homes = sum(Homes),
            Pop = sum(Pop)) %>%
  mutate(HomesPerc = Homes/sum(Homes),
         PopPerc = Pop/sum(Pop))

EnglandCompTab

xtable(EnglandCompTab, caption="Summary of effecrt across England",
       label = "tab:EnglandCompTab") %>% 
  print(., type="latex", file=file.path(TexTables,"EnglandCompTab.tex"))



#Observed
Combine1ExO %>%
  group_by((absdiff>0)) %>%
  summarise(mean = mean(HomePrice),
            median = median(HomePrice),
            Homes = sum(Homes),
            Pop = sum(Pop)) %>%
  mutate(HomesPerc = Homes/sum(Homes),
         PopPerc = Pop/sum(Pop))

```



```{r}

test <-ls(pattern = "DATA") %>%
  map_df(~get(.x) %>%
           group_by(LAD11CD) %>%
           mutate(LowUsePercentile = percent_rank(LowUsePerc),
                  MeanPricePercentile = percent_rank(MeanPrice)))

cor(test$LowUsePerc,test$MeanPrice,"complete.obs")
cor(test$LowUsePerc,test$MedianPrice, "complete.obs")

cor(test$LowUsePercentile,test$MeanPricePercentile , "complete.obs")


test %>%
  ggplot(aes(x= LowUsePercentile, y = MeanPricePercentile)) +geom_point()

test <-ls(pattern = "DATA") %>%
  map_dbl(~{ df <-get(.x)
    cor(df$LowUsePerc,df$MeanPrice,"complete.obs", method = "kendall")
  })

  plot(density(abs(test)))
  
  
  Combine1ExO %>%
    ggplot(., aes(x = absdiff>0 )) +geom_bar()
  
```

