---
title: "Untitled"
author: "Jonathan Bourne"
date: "5 July 2017"
output: html_document
---

new article and paper on airbnb effecr
https://www.citylab.com/equity/2018/03/what-airbnb-did-to-new-york-city/552749/?utm_source=atlfb

Islington should be removed and put back in when they send the correct data, it is giving a false negative

#this uses rank for distance from LAD I think it should be dist check this


Intellectual property rights and
disclosures under the Freedom of
Information Act

16. It may not be apparent to recipients that the information is
protected by copyright. Therefore when a public authority
wishes to protect its own copyright, or the copyright is owned
by a third party, it should advise the applicant that the
information remains copyright protected.


Please can you provide excel the file sent to Jonathan Bourne on xxx

The reference number for this case is xxx.

Yours faithfully,

Jonathan Bourne


#ico complaint ref
fs-506-897-47

#OGL licence claim

All data used in this paper is covered by the Open Government Licence.

The Data meets all 4 criteria described in section 56 of "Datasets (sections 11, 19 & 45)" FOI guidance document.
These criteria are that the data is held by the authority, The data is part of a relveant copyright work (The data is held in a databse), the authority holds the copyright to the data (The information in the database is owned by the local council). 
As local authorities are public sector bodies (shown in the public sector classification guide) and that council tax is a core task, normally the data would be covered by the RPSI. However, following section 5 of the Re use of public sector infrmation regulations 2015.

"5.—(1) These Regulations do not apply to a document where—

(a)the activity of supplying the document is one which falls outside the public task of the public sector body, provided that the scope of the public task of that body is transparent and subject to review; or""

As the document the councils needed to complete is custom made and not part of the public task, the RPSI does not cover the resultant work and licencing reverts to the FOIA. 
The FOIA states that a specific licence must be given for all datasets released under the act. As no charge has been levied against the use of the data then the default Open government licence is applied following section 69 of the "Datasets (sections 11, 19 & 45)" FOI guidance document.


#Setup

```{r setup}
setwd( "~/Dropbox/SSE/Empty Homes/EmptyHomesCode/SubCode")
source("Setup.R")

setwd(Functions)
list.files() %>% map(source)

Figures <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Empty Homes Write up 2/Figures" #file.path(basewd, "Figures")
TexTables <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Empty Homes Write up 2/Tables"
source(file.path(CommonCode, "AuxdataLoad.R"))


```


#Cumbria
```{r}
setwd(file.path(RegionsComp, "Region North West"))

BarrowCUMBRIADATA <- read_excel("Barrow-in-FurnessExemptionsLSOA.xlsx", sheet=1)[1:4]%>%  
  StructureData(.,lowuse = c(2:6,8))

SLakelandCUMBRIADATA <- read_excel("South LakelandExemptionsLSOA.XLSX", sheet=1)[,1:4] %>%
    StructureData(., lowuse=2:9)

#only inlcudes postcodes so the mergeing needs to be done manually
CopelandCUMBRIADATA <- read_excel("CopelandFOI 5778 data 100517 CBC.XLSX", sheet=1) %>% 
  mutate(Postcode = sub(" ", "", Postcode)) %>%
  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=`Disc Type Ind`, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
  StructureData()


EdenCUMBRIADATA <- read_excel("EdenDiscountsLSOA.xlsx"  , sheet=1)[1:4] %>%  
  StructureData(.,lowuse = c(2:6,8))

CarliseCUMBRIADATA <- read_excel("FOI 5846 5983-CarlisleDiscountsLSOA June 2017.xlsx"  , sheet=1)[1:4] %>%  
  StructureData(.)

AllerdaleCUMBRIADATA <- read_excel("F17.132_Copy of Allerdale discounts LSOA_170815.xlsx"  , sheet=1)[1:4] %>%  
  StructureData(c(4:10))

```


#Manchester

```{r}
list.files()

OldhamMANCDATA <- read_excel("FOI 10635 OldhamDiscounts LSOA.xlsx", sheet = 1 )[c(1,4:6)] %>%  
  StructureData(., c(5:6,8:11))

ManchesterMANCDATA <- read_excel("ManchesterDiscountsLSOA.xlsx", sheet = 1 )[1:4] %>%  
  StructureData(. )

RochdaleMANCDATA <- read_excel("Rochdale Both.xlsx" , sheet = 1 )[1:4] %>%  
  StructureData(., c(5,6,14,15,20:22))

TamesideMANCDATA <- read_excel("Tameside FOI 6257A2.xlsx", sheet = 1 )[1:4] %>%  
  StructureData(. )

TraffordMANCDATA <- read_excel("Trafford Exemption and Levy.xlsx" , sheet = 1 )[1:4] %>%
  filter(Exemption_type =="LEVY") %>% 
  bind_rows(.,read_excel("TraffordDiscountsLSOA.XLSX", sheet = 1 )[1:4] %>% rename(Exemption_type = Class)) %>%
  StructureData()

WiganMANCDATA <- read_excel("Wigan 5528 DISCOUNTS.xlsx", sheet = 1 )[1:4] %>%  
  StructureData(., lowuse = c(2:3, 5:9) )


#hide plot
#ls(pattern = "MANC") %>% map_df(~eval(parse(text=.x))) %>% PlotMap(., AG)


```


#West Midlands Brum
```{r}

setwd(file.path(RegionsComp, "Region West Midlands"))

SandWellDATA <- read_excel("FOI - SandwellDiscountsLSOA - FS57000079 Disc.xlsx" )[1:4] %>%  
  StructureData(2:6)

WolverhamptonDATA <- read_excel("WolverhamptonDiscountsLSOA.XLSX"  )[1:4] %>%  
  StructureData(c(2:5,7))

WalsallDATA <- read_excel("WalsallDiscountsLSOA.XLSX" )[1:4] %>%  
  StructureData(c(4:5,7:8))

BirminghamDATA <-  read_excel("Birmingham CT EMPTIES.xlsx" )%>%
mutate(Postcode = gsub(" ", "", `Post Code`)) %>%
 left_join(.,PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=`Current Discount Type Description`, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Country_code, Admin_district_code) %>%
  StructureData(c(2,4:9))

DudleyDATA <- read_excel("Completed DudleyDiscountsLSOA.xlsx"  )[1:4] %>%  
  StructureData()

```


#SouthWest

##Cornwall

```{r}

setwd(file.path(RegionsComp, "Region South West"))

CornwallDATA <- read_excel("Cornwall.xlsx", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
  StructureData(lowuse = c(2,23:28))
```

##Devon

```{r}

NorthDevonDATA <- read_excel("North DevonDiscountsLSOA.XLSX", sheet=1)[1:4] %>%
  StructureData  

PlymouthDATA <- read_excel("PlymouthDiscountsLSOA.XLSX" , sheet=1)[1:4] %>%
  StructureData(lowuse = 4:8)

TorbayDATA <- read_excel("Torbay_discounts 1718551.xlsx"  , sheet=1)[1:4] %>%
  StructureData()

MidDevonDATA <- read_excel("MidDevon FOI04942Information 3.xlsx" , sheet=1)[1:4] %>%
  StructureData(c(7,10:11,20:22,26,28))

TorridgeDATA <- read_excel("FOI_TorridgeDiscountsLSOA.XLSX" , sheet=1)[1:4] %>%
  StructureData(c(4:5,7:10,13))

```

##Somerset

```{r}
NorthSomsertDATA <- read_excel("1501796 North SomersetDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
  StructureData(lowuse= 2:6)  

MendipDATA <- read_excel("Mendip 356 20170706 Response.xlsx" , sheet=1)[1:4] %>%
  StructureData(lowuse= c(37:39,52:54,65:66,69)) 

#Bristol appears to have not included second homes
#BristolDATA <- read_excel("Bristol%2c City ofDiscountsLSOA_as at 110817.xlsx")[c(1:4)] %>%
#  StructureData()

```


##Dorset

```{r}
BournemouthDATA <- read_excel("BournemouthDiscountsLSOA_R.xlsx" )[1:4] %>%
  StructureData(c(6,8,9:13))

PooleDATA <- read_excel("Copy of FOI - 265 - Bourne - PooleDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
  StructureData(lowuse = c(5,11:14,18))

ChristchurchDATA <- read_excel("Christchurch FOI17 - 0312 - Bourne - Ctax Discounts and Exemptions.xls",
                               sheet=1)[1:4] %>%
  StructureData(lowuse = c(6,12:17,20))

WeymouthDATA <-  read_excel("63687 Weymouth and PortlandDiscountsLSOA - 010817.xlsx"    ,
                               sheet=1)[1:4] %>%
  StructureData()

WestDorsetDATA <-  read_excel("47019 West DorsetDiscountsLSOA - 010817.xlsx"     ,
                               sheet=1)[1:4] %>%
  StructureData()



PurbeckDATA <-  read_excel("PurbeckDiscountsLSOA - 010817.xlsx"      ,
                               sheet=1)[1:4] %>%
  StructureData()

```


##Wiltshire

```{r}
#Wiltshire have not included everything
WiltshireDATA <- read_excel("Wiltshire ENQ07536 - Council tax discounts 2.xlsx",
                               sheet=1)[1:4] %>%
  StructureData(lowuse = 3:8)

SwindonDATA <- read_excel("Swindon - 7th July 2017 - Part 2 (Discounts).xlsx" ,
                               sheet=1)[1:4] %>%
  StructureData(2:6)
```

#East of England

##Suffolk


```{r}
setwd(file.path(RegionsComp, "Region East of England"))
list.files()


#Serparete in to the two LADS
# CoastWaveDATA <- bind_rows(read.xlsx("FOI IMT178324 SuffolkCoastal.xlsx")[1:4] , read.xlsx("FOI IMT178324 Waveney.xlsx")[1:4]) %>% setNames(make.names(names(.))) %>%
#   mutate(Exemption.type = Exemption.type %>% trimws %>%
#            make.names %>% 
#            gsub("\\.{2,}" , ".", .))  %>%
#   StructureData(., lowuse = c(5,6,13,14,16:18))

CoastSUFFDATA <- read.xlsx("FOI IMT178324 SuffolkCoastal.xlsx")[1:4] %>% setNames(make.names(names(.))) %>%
  mutate(Exemption.type = Exemption.type %>% trimws %>%
           make.names %>% 
           gsub("\\.{2,}" , ".", .))  %>%
  StructureData(.,c(5,6,11,12,14:16))

WaveneySUFFDATA <- read.xlsx("FOI IMT178324 Waveney.xlsx")[1:4] %>% setNames(make.names(names(.))) %>%
  mutate(Exemption.type = Exemption.type %>% trimws %>%
           make.names %>% 
           gsub("\\.{2,}" , ".", .))  %>%
  StructureData(., lowuse = c(5,6,13,14,16:18))

StEdmundsDATA <- read.xlsx("se FOI 146  3948502_Copy+of+St+EdmundsburyDiscountsLSOA.xlsx")[1:4] %>%
  StructureData()

ForestHeathDATA <- read.xlsx("FH FOI 146 Discounts.xlsx")[1:4] %>%
  StructureData()

IpswichDATA <- read_xlsx("IpswichDiscountsLSOA.xlsx")[1:4] %>%
   StructureData(c(2:4,6:11,13:15))

#Mid Suffolk and Babergh
#These have been combined and are just the postcodes so need to be fixed
#Missing loads of postcodes
MidSuffolkDATA <- read_excel("MidSuffolk FOI MF379 1718 Discount.xlsx") %>%
mutate(Postcode = gsub(" ", "", `Post Code`)) %>%
 left_join(.,PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=`Discount Type Description`, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Country_code, Admin_district_code) %>%
  StructureData(c(2:12,14:15))


BaberghDATA <- read_excel("Babergh FOI BF378 1718 Discount.xlsx")%>%
mutate(Postcode = gsub(" ", "", `Post Code`)) %>%
 left_join(.,PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=`Discount Type Description`, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Country_code, Admin_district_code) %>%
  StructureData(c(2:6,8:11,13:15))


```

##Norfolk
```{r}
#This is being checked
BroadlandsDATA <- read_excel("BroadlandDiscountsLSOA.xlsx", sheet=1)[1:4] %>%
  StructureData(4:9)

KingsLynnDATA <- read_excel("197782 - King s Lynn and West NorfolkDiscountsLSOA (2).xlsx" , sheet=1)[1:4] %>%
  StructureData(2:11)

NorthNorfolkDATA <- read_excel("North NorfolkDiscountsLSOA.XLSX" , sheet=1)[1:4] %>%
  StructureData()

BrecklandsDATA <- read_excel("BFOI-003031 BrecklandDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
  StructureData()

SNorfolkDATA <- read_excel("SNorfolk 17-307 Discounts.xlsx"  , sheet=1)[1:4] %>%
  StructureData()


NorwichDATA <- read_excel("Norwich Discounts FINAL.xlsx"  , sheet=1)[1:4] %>%
  StructureData(2:8)


```


##Cambridge
```{r}
EastCambsDATA <- read_excel("EC FOI 130 - DISC_FOI_0_3944413b.xlsx", sheet=1)[1:4] %>%
  StructureData()


FenlandDATA <- read_excel("FL FOI 4544 DISCOUNTS.XLSX" , sheet=1)[1:4] %>%
  StructureData()

HuntingdonDATA <- read_excel("Huntingdonshire  FOI 568discounts.xlsx" , sheet=1)[1:4] %>%
  StructureData(lowuse = 2:8)

PeterboroughDATA <- read_excel("Peterborough 1707267585 completed.xlsx" , sheet=1)[1:4] %>%
  StructureData(lowuse = c(4,6:7,11))

CambridgeDATA <- read_excel("566 - Copy of Copy of CambridgeDiscountsLSOA .xlsx" , sheet=1)[1:4] %>%
  StructureData(2:5)

```

#South East


```{r}

setwd(file.path(RegionsComp, "Region South East"))
list.files()

BrightonDATA <- read_excel("Copy of Brighton and HoveDiscountsLSOA (4).xlsx", sheet=1)%>% .[,c(2,3:5)] %>%
  StructureData(lowuse = 2:8)
#MakeLeaflet(BournemouthDATA)


ValeWhiteDATA <- read_excel("Vale of White HorseDiscountsLSOA (00000002).xlsx" , sheet=1)[1:4] %>%
  StructureData(c(5,7,8,9,10,14))

SouthOxfordDATA <- read_excel("South OxfordshireDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
  StructureData(c(5,7,8,9,10,14))

```


#Yorkshire and the Humber
```{r}
setwd(file.path(RegionsComp, "Region Yorkshire and The Humber"))

#Hull

HullDATA <-read_excel("KINGSTON UPON HULL%2c CITY OFDISCOUNTSLSOA.XLSX")[-c(c(1:6)),1:4] %>%
  StructureData(.)

#Harrowgate

HarrogateDATA <-read_excel("Harrogate DiscountsExemptionsLSOA.xlsx" )[,1:4] %>%
  StructureData(.,3:10)

#Selby
SelbyDATA <-read_excel("SelbyExemptionsLSOA.xlsx" )[,1:4]%>%
  StructureData(20:27)


# HambletonDATA <- read_excel("HDC1088.xlsx")[,1:4] %>%
#  StructureData()

ScarboroughDATA <- read_excel("FOIA 5156 Scarborough Discounts LSOA.xlsx"  )[,1:4]%>%
  StructureData(2:8)



# Middlesbrough sent the wrong data
# MiddlesbroughDATA <- read_excel( "Middlesbrough FOI RES - 011397 Discounts.xlsx"   )[,1:4]%>%
#   StructureData()

#Ryedale
RyedaleDATA <-  read_excel("Ryedale FOI 4597.xlsx")[,1:4]%>%
  StructureData(2:6)

#Crave they sent full addresses by mistake I'll do a temporary fix
CravenDATA <- read_excel("Craven Discounts.xlsx" ) %>%
  setNames(make.names(names(.))) %>%
  mutate(Postcode = str_split(Full.Property.Address, "(,)(?!.*,)", simplify = T)[,2] %>% 
           gsub(" ", "", .)) %>%
  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=Discount.Type.Description, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
  StructureData(c(2:5,7))

#Redcar and cleveland

RedcarDATA <-  read_excel("Redcar 0614 attachment 1.xlsx")[,1:4]%>%
  StructureData(2:10)


CalderdaleDATA <- read_excel("Copy of CalderdaleDiscountsLSOA.xlsx" )[,1:4]%>%
  StructureData(c(7,10,22:25))

BradfordDATA <- read_excel("Copy of BradfordDiscountsLSOA.xlsx")[1:4] %>%
  StructureData(c(2:7))


RichmondshireDATA <- read_excel("Richmondshire FOI 4960.xls", col_names = FALSE)[1:2] %>%
    setNames(c("Exemption.type", "Postcode")) %>%
  mutate(Postcode = sub(" ", "", Postcode)) %>%
  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
  StructureData(lowuse = c(2:7))
  

KirkleesDATA <- read_excel("Jonathan Bourne KirkleesDiscountsLSOA Complete.xlsx" )[1:4] %>%
  StructureData(2:5)

WakefieldData <-  read_excel("WakefieldDiscountsLSOA.xlsx" )[1:4] %>%
  StructureData(2:7)

```

#North East

##Tyneside

```{r}

setwd(file.path(RegionsComp, "Region North East"))
list.files()
#Not sure all are there ask for confirmation
 SunderlandDATA <- read_excel("Sunderland Freedom of Informaton Request from Jonathan Bourne- 17-07-21-Discounts.xlsx"  , sheet=1)%>% .[,1:4] %>%
   StructureData(lowuse = c(2:4,6,8:10))


NewcastleDATA <- read_excel("Newcastle upon TyneDiscountsLSOA.xlsx", sheet=1)%>% .[,c(1,3:5)] %>%
    StructureData(lowuse = 2:7)


#FOr some reason Gateshead has the wrong LAD11CD I don't know why. I have changed it to the right one but feel that perhaps I should check them all, but how?
GatesheadDATA <- read_excel("Copy of GatesheadExemptionsLSOA.XLSX"   , sheet=1)%>% .[,1:4] %>%
   StructureData(lowuse = c(2:3, 20,22:25)) %>%
  mutate(LAD11CD = ifelse(is.na(LAD11CD), NA, "E08000037"))

STynesideDATA <- read_excel("FOI 17.18456 - South Tyneside Discounts.xlsx", sheet=1)[,c(1,4:6)] %>%
    StructureData(c(32:35,38))

```


##Northumberland

```{r}
NorthumberlandDATA <- read_excel("FOI 2762 data NorthumberlandDiscounts.xlsx", sheet=1)%>% .[,1:4] %>%
    StructureData(2:7) %>%
  #The LAD code is wrong for some reason
  mutate(LAD11CD = "E06000057")

```


##Durham
```{r}
  
DurhamDATA <- read_excel("County DurhamDiscountsLSOA.XLSX" , sheet=1) %>% .[,c(1,4:6)] %>%
    StructureData()

  DarlingtonDATA <- read_excel("Darlington DBC-0809-17.xlsx" , sheet=1) %>% .[,1:4] %>%
    StructureData()

  HartlepoolDATA <- read_csv("FOI 7942 HartlepoolDiscountsLSOA.csv") %>% .[,1:4] %>%
    StructureData(2:7)
  

```


#Wales

```{r}

setwd(file.path(RegionsComp, "Region Wales"))
list.files()

#Ceredigion completed some major Student Halls which were transferred to the University, this created some very large B type transfers which artificially push the cost of second homes lower than the price of regular homes.

CeredigionDATA <- read_excel("CTAX - Ceredigion Discounts LSOA.xlsx", sheet=1)%>% .[,1:4] %>%
  StructureData(lowuse =c(8:13,15))

MonmouthDATA <- read_excel("MCC Discounts Jul 17.xlsx", sheet=1)%>% .[,1:4] %>%
  StructureData(lowuse = c(4:8))


#includes the zero class which is descibeed as 
#ZERO – tis is a 50% reduction which applies after exemptions that are time limited, have expired. They are awarded on the basis that the property remains unoccupied and unfurnished.
  CarmarthenDATA <- read_excel("CarmarthenshireDiscountsLSOA.XLSX" , sheet=1)%>% .[,1:4] %>%
    StructureData()

#Strangely low numbers checking
# PowysDATA <- read_excel("PowysDiscountsLSOA.XLSX"    , sheet=1)%>% .[,1:4] %>%
#   StructureData(lowuse = c(3,5:6))

#It seems Conwy really is this short on the discounts  
ConwyDATA <- read_excel("Conwy FOI 0260-17.xlsx" , sheet=1) %>%
  rename(Postcode = geo_postcode) %>%
  mutate(Postcode = sub(" ", "", Postcode)) %>%
  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=disc_type_desc, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
  StructureData(lowuse = c(2,4))

DenbigshireDATA <- read_excel("FOI 2503 Denbighshirev2 .xlsx" , sheet=1)%>% .[,1:4] %>%
    StructureData(c(8:9,11,13))

WrexhamDATA <- read_csv("WrexhamDiscountsLSOA.csv" )%>% .[,1:4] %>%
    StructureData(2:5)

#Pembrokeshire didn't send all the data
PembrokeshireDATA <- read_excel("Copy of PembrokeshireDiscountsLSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
    StructureData(3)

FlintshireDATA <- read_excel("FOI R014329 FlintshireDiscounts LSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
    StructureData()


```


# London using the full data

```{r}
#Source the code from another file as it is very long
source(file.path(CommonCode, "LondonFullProcesss.R"))

#MakeLeaflet(NewhamLONDATA)

```

#Semi data 

The LSOA will be assigned empty and low use homes by percentage

```{r}
#ward folder
setwd(SemiLondon)


wardnames <- EW2 %>% group_by(Admin_ward_code, WD16NM) %>% summarise(counts = n(), LAD11NM = first(LAD11NM), LAD11CD = first(LAD11CD)) %>% arrange(WD16NM)


#TowerHamlets
TowerLONDATA <- read_excel("Towerhamlets.xlsx")[,c(1,3)] %>% 
  filter(!is.na(DiscClass)) %>%
  group_by(Ward, DiscClass) %>%
  summarise(count = n()) %>% ungroup %>%
  spread(., key =DiscClass, value = count, fill = 0 ) %>% 
  mutate(Empty = rowSums(.[,4:8]), LowUse = B+BE+Empty) %>% 
  slice(c(1:13, 15:17, 14, 18:20)) %>%
   bind_cols(., wardnames %>% filter(grepl("Tower", LAD11NM))) %>%
  SemiDataStructure


HaveringLONDATA <- read_excel("AIR12965P Informatiion provided by Council Tax.xlsx" ) %>%
  rename(DiscClass = X__1) %>%
  select(-Mawneys, -`Aveley & Uplands`, -Whalebone) %>%
  gather(key = "ward", value = "counts", -DiscClass) %>%
  spread(key= DiscClass, value = counts, fill = 0) %>%
  mutate(Empty = rowSums(.[,c(5:6,14,17)]), LowUse = Empty+ `Second Home Class A`+ `Second Homes Class B`) %>% 
  bind_cols(., wardnames %>% filter(grepl("Havering", LAD11NM))) %>%
  SemiDataStructure

```

General Stats
#UK population


```{r}

#number of LUPS and Total Homes
DataCover <- ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x))) %>% 
  filter(!is.na(LAD11NM)) %>%
  summarise(
           'LADs' = length(ls(pattern = "DATA", envir = globalenv())), #bits of other LADS cause the number to be higher than reality so the ls function is used again
           '% of all LADs' = length(ls(pattern = "DATA", envir = globalenv()))/(EW2$LAD11NM %>% unique %>% length())*100,
           LUPs = sum(LowUse, na.rm = T),
           Homes = sum(Homes, na.rm = T),
           '% of all Homes' = Homes/sum(EW2$Homes)*100,
           Population = sum(Pop, na.rm= T),
           '% of total population' = Population/sum(EW2$Pop)*100) %>%
  mutate_if(.<1, funs(signif(.,3))) %>%
  mutate_if(.>1, as.integer) %>%
  mutate_all(as.character) %>% 
  gather 

DataCover 

xtable(DataCover, caption="Summary of collected data coverage",
       label = "tab:DataCover") %>% 
  print(., type="latex", file=file.path(TexTables,"DataCover.tex"))

#Percentage of EW LADS
length(ls(pattern = "DATA"))/(EW2$LAD11NM %>% unique %>% length())

#check which lads are present even though I don't have data due to postcode matching
#test <- ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x)))  %>% arrange(LAD11NM)
#unique(test$LAD11NM)

```


#Plot stuff
```{r}
x <-bind_rows(SouthwarkLONDATA, TowerDATA, LambethLONDATA, CoLLONDATA, NewhamLONDATA) %>% MakeLeaflet

z<- MakeLeaflet(AllerdaleDATA)
z
# 
setwd(basewd)
 saveWidget(z, file=file.path(basewd, "Cumbria.html"), selfcontained = TRUE )

#testSouth <- DistribCompareBootstrapper(SouthwarkLONDAls(pattern = "DATA")TA, 1652, 1000)
testSouth %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100) %>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

ValueTtest(test)

PlotMap(ConwyDATA)

z <-ChelseaLONDATA %>% 
  mutate(LAD11CD = ifelse(LAD11CD  == "E09000005", "E05009388" ,LAD11CD)) %>% #kept adding in Barnet
  filter(LAD11NM =="Kensington and Chelsea") %>% 
  MakeLeaflet()

mapshot(z, file = file.path(Figures, "Chelsea.pdf"))

CumbriaPlot <- ls(pattern = "CUMBRIA") %>% 
  map_df(~get(.x)) %>%
   group_by(LSOA_CODE) %>%
   summarise(LowUse = sum(LowUse, na.rm = TRUE)) %>% 
  CalcLowUse()

z<- MakeLeaflet(CumbriaPlot)

mapshot(z, file = file.path(Figures, "Cumbria.pdf"))



z<- MakeLeaflet(CornwallDATA)
mapshot(z, file = file.path(Figures, "Cornwall.pdf"))

z<- MakeLeaflet(BarrowCUMBRIADATA)
mapshot(z, file = file.path(Figures, "Barrow.pdf"))


MakeLeaflet(ConwyDATA)

```

#Look at saleries
```{r}

unafford <- ls(pattern = "DATA") %>%
  map_df(~get(.x) %>% select(LowUse:WardLowuseClass)) %>%
  group_by(MSOA11CD) %>%
  summarise(LowUse = sum(LowUse, na.rm = T),
            Homes = sum(Homes, na.rm = T),
            Pop = sum(Pop, na.rm = T)) %>%
  mutate(LowUsePerc = LowUse/Homes) %>%
  left_join(IncomeEst, by = "MSOA11CD") %>%
  mutate(decile = ntile(ratio, 20))


unaffordExLon <- unafford %>%
  filter(Region.name != "London") %>%
  mutate(decile = ntile(ratio, 50))

#London follows the same pattern it just happens further up the scale
unaffordLon <- unafford %>%
  filter(Region.name == "London") %>%
  mutate(decile = ntile(ratio, 50))

cor(unaffordExLon$LowUsePerc, unaffordExLon$ratio)
cor(unafford$Yearly.income, unafford$ratio, "complete.obs")

cor(unaffordExLon$LowUsePerc, unaffordExLon$MedianPrice)
cor(unaffordExLon$Yearly.income, unaffordExLon$MedianPrice)
cor(unafford$Yearly.income, unafford$MeanPrice, "complete.obs")


test <- lm(MedianPrice ~ LowUsePerc + Yearly.income, data  = unafford)

summary(test)

decile <- bind_rows(mutate(unaffordExLon, type = "Excluding London"), 
                    mutate(unafford, type = "Including London"),
                    mutate(unaffordLon, type = "Only London")) %>%
    group_by(type) %>%
    mutate(decile = ntile(ratio, 50)) %>%
      group_by(decile, type) %>%
    summarise(mean = mean(LowUsePerc),
              median = median(LowUsePerc),
              counts = n(),
              ratio= mean(ratio)
              ) %>%
  mutate(decile2 = decile^2,
         ratio2 = ratio^2,
         logval = log(decile),
         expval = exp(decile),
         expvalneg = exp(-decile)) %>%
  filter(!is.na(decile))

#Looking at the relationship between unaffordability and LUP percentage

decile %>% 
#  filter(type == "Only London") %>% 
  ggplot(aes(x= decile, y = median)) + 
  facet_grid(.~type) + 
  #geom_point(data =unaffordExLon , aes(x= decile, y = LowUsePerc), alpha = 0.2 )+
  geom_point(aes(colour = type))  +
  labs(x = "2 percentile group", y = "median Percent Low Use") + 
  theme(legend.position= "none") + 
  geom_smooth(method="loess",se=FALSE, colour = "black")
SaveFig("LowUsePercVSratio.pdf")

decile %>% 
  filter(type == "Excluding London") %>% 
  ggplot(aes(x= ratio, y = median)) + 
  facet_grid(.~type) + 
  #geom_point(data =unaffordExLon , aes(x= decile, y = LowUsePerc), alpha = 0.2 )+
  geom_point(aes(colour = type))  +
  labs(x = "ith 2 percentile group", y = "median Percent Low Use") + 
  theme(legend.position= "none") + 
  geom_smooth(method="loess",se=FALSE, colour = "black")


#model fit
decile %>% 
    filter(type == "Excluding London") %>% 
  lm(median~decile +decile2, data = .) %>% summary

#model fit
decile %>% 
    filter(type == "Excluding London") %>% 
lm(median~ratio + ratio2, data = .) %>% summary

decile %>% 
    filter(type == "Excluding London") %>% 
lm(median~expval + expvalneg, data = .) %>% summary

#make nonlinear  model
mod <- decile %>% 
    filter(type == "Excluding London") %>% 
  nls(median ~ exp(a + b*decile)+  exp(d + c*decile), data = ., 
      start = list(a = 0, b = -3, c = 0, d = 0))

mod2 <- decile %>% 
    filter(type == "Only London") %>% 
  nls(median ~ exp(a + b*decile), data = ., 
      start = list(a = 0, b = -3))

summary(mod)

decile %>%
      filter(type == "Excluding London") %>% 
  ggplot(aes(x = decile, y = median))+
  geom_point() +
  geom_line(aes(y = predict(mod, list(x = decile))))


unafford %>%
  ggplot(aes(x= ratio, y = MeanPrice)) + geom_point()

#Example of the theoretical relationship

data_frame(Index = 1:100) %>%
  mutate(Primary = exp(-0.05*(Index))+0.05, 
         Auxilary = (exp(Index/100)-1),
    Total = Primary + Auxilary) %>%
  gather(key = "Type", value = "value", -Index) %>%
  ggplot(aes(x= Index, y = value, colour = Type )) +
  geom_line() +
  labs(title = "LUP percentage as a function of primary and Auxilary demand",
       x = "Demand",
       y = "LUP percentage") +
  theme(
  axis.text.x = element_blank(),
  axis.text.y = element_blank()
  )
SaveFig("TheoreticalDemand.pdf")


unaffordLAD <- unafford %>%
  rename(LAD11CD = Local.authority.code) %>%
  group_by(LAD11CD) %>%
  mutate(TotInc = Yearly.income*Pop) %>%
  summarise(TotInc = sum(TotInc),
            Pop = sum(Pop)) %>%
  mutate(meanInc = TotInc/Pop)

```


#Bootstrap

Now all the data is loaded each LAD needs to be bootstrapped

```{r}

setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootStrapAuthorities")
  
#Find what needs to be bootstrapped
BootStrapFiles <- list.files(getwd()) %>% gsub("DATA.rds", "",.)
  newLADsnames <- sub("DATA", "", ls(pattern = "DATA", envir = globalenv())) %>% 
    .[!(. %in% BootStrapFiles)] 
  newLADs <- paste0(newLADsnames, "DATA") 

  
   #only bootstrap if there is something to add.
  #Save each boostrap as you go along to avoid losing it all in a crash
  if(length(newLADsnames)>0){
    newLADs  %>% walk(~{print(.x)
      DistribCompareBootstrapper(get(.x), 1652, 1000, type=NULL, PropertyTypes)%>%
      saveRDS(., file = paste0(.x, ".rds"))
      }) 
  }

  #once all Bootratps complete load them all into a list
 BootStrapRES <- list.files(getwd()) %>%
   map(~readRDS(.x))
 
 #name the list
 names(BootStrapRES) <- list.files(getwd()) %>% gsub(".rds", "",.)


BootStrapRESExO <- BootStrapRES
#Should clean up and remove EXO
rm(BootStrapRES)

#Make a summary dataframe
Combine1ExO <- BootResSummaryData(BootStrapRESExO) 



```


#Make class plots of bootstrap results

```{r}
test <- BootStrapRESExO$WestminsterLON %>% 
  group_by(class) %>%
  summarise_all(funs(mean))


test2 <- test %>%
  select(-class) %>%
  summarise_all(funs(sum)) %>%
  mutate(LowUseValue = LowUseValue/1e9)


#99% of the LADs are significantly different from 0 at the 95% level
sum(Combine1ExO$Ttest.p.value>0.975 |Combine1ExO$Ttest.p.value<0.025)/nrow(Combine1ExO)

PlotClassDiff(BootStrapRESExO$ChelseaLON, "Kensington and Chelsea")
SaveFig("ClassdiffChelsea.pdf")

PlotClassDiff(BootStrapRESExO$Cornwall, "Cornwall")
SaveFig("ClassdiffCornwall.pdf")

PlotClassDiff(BootStrapRESExO$BarrowCUMBRIA, "Barrow")
SaveFig("ClassdiffBarrow.pdf")

test <- BootStrapRESExO %>% 
  bind_rows %>%
  select(-LAD11CD) %>%
  group_by(class, ID) %>%
  summarise_all(sum) %>%
  ungroup %>%
  mutate(HomesPrice = HomesValue/Homes,
         LowUsePrice = LowUseValue/LowUse,         
         ratio = LowUse/Homes,
         HomesPerc = Homes/sum(Homes, rm.na = T),
         LowUsePerc = LowUse/sum(LowUse, rm.na = T),
         ClassPerc = LowUse/Homes,
         ExpectedHomes = HomesPerc*sum(LowUse, rm.na = T),
         RatioExvsAct = LowUse/ExpectedHomes
         ) %>%
        mutate(class = fct_relevel(class,c("Lower", "Mid", "Upper", "Prime", "Super")),
               LUPmore = RatioExvsAct>1)

test2 <- test %>% group_by(class) %>%
  summarise_all(mean)

PlotClassDiff(test)
SaveFig("ClassdiffAllData.pdf")


test %>% 
  mutate(RatioExvsAct = LowUsePrice/HomesPrice) %>%
   mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
     ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + 
     geom_boxplot() + 
     labs(title = "Observed within class difference in Price from expected for LUPs")
SaveFig("PricediffAllData.pdf")


#Total value of homes and LUPS

LADnames <- names(BootStrapRESExO)

LUPval <-   map2(.x =BootStrapRESExO, .y =   names(BootStrapRESExO),~ {.x %>% mutate(LAD  = .y)}) %>%
  bind_rows %>%
  select(-class, -LAD11CD) %>%
  group_by(LAD, ID) %>%
  summarise_all(sum) %>%
  group_by(LAD) %>%
  summarise_all(mean) %>%
  ungroup %>%
  mutate(HomesPrice = HomesValue/Homes,
         LowUsePrice = LowUseValue/LowUse,         
         ratio = LowUse/Homes,
         HomesPerc = Homes/sum(Homes, rm.na = T),
         LowUsePerc = LowUse/sum(LowUse, rm.na = T),
         ClassPerc = LowUse/Homes,
         ExpectedHomes = HomesPerc*sum(LowUse, rm.na = T),
         RatioExvsAct = LowUse/ExpectedHomes
         ) %>%
  mutate(VancouverTax = LowUseValue*0.01/1000)


#value is billions of pounds of a vancouver tax in England and wales.
LUPval$VancouverTax %>% sum(.)/1000

```



#Explore results

This chunk calculates for both A and B

```{r}

LADNMs <- EW2 %>% group_by(LAD11CD) %>%
  summarise(LAD11NM = first(LAD11NM))

PropertyTypes <- c("D", "S", "T", "F")

#calulcate the number of properties sold and the mean price
ABratio <- prices %>% 
  filter(X5 %in% PropertyTypes) %>%
  group_by(Admin_district_code, X15) %>%
  summarise(count = n(), 
            mean = mean(X2)) %>%
  rename(LAD11CD = Admin_district_code)

ABratio2 <- ABratio%>%
  select(-mean) %>%
spread(key = X15, value = count) %>%
  mutate(Countratio = B/(A+B)) %>%
  rename(CountofA = A, CountofB = B)

ABratio3 <- ABratio%>%
  select(-count) %>%
spread(key = X15, value = mean) %>%
  mutate(Valueratio = B/(A)) %>%
  rename(MeanofA= A, MeanofB = B)


CombineAB <-left_join(ABratio2, ABratio3, by = "LAD11CD") %>%
  left_join(Combine1ExO, ., by = "LAD11CD") 

rm(ABratio); rm(ABratio2); rm(ABratio3)


```


#Inlcuding deprivation
```{r}

#creating the empty deprivation extent
maxLSOA <- max(LSOADep$Rank..where.1.is.most.deprived.)

ExtentWeight <- LSOADep%>%
  mutate(percentile = (Rank..where.1.is.most.deprived./maxLSOA),
         perc2 = percentile-0.11,
         weight = ifelse(percentile<.11|percentile>.3,0, 0.95 - (0.95/.20)*perc2 ),
         weight = ifelse(percentile<0.11, 1, weight)) %>%
  select(LSOA_CODE, weight)

#Create the extent of deprivation of the LUPs
LUPdepExt <- ls(pattern = "DATA") %>% map_dbl(~{
df <- get(.x)
test <- df %>% 
  left_join(., ExtentWeight, by= "LSOA_CODE")  %>%
  mutate(WeightedLUP = (LowUse*weight)/sum(LowUse))

sum(test$WeightedLUP, na.rm = TRUE)
})


#Add in deprivation
Combine1ExO <- select(LADDep, LAD11CD ,Extent) %>% 
  left_join(CombineAB, ., by = "LAD11CD") %>%
  mutate(LUPdepExt) 

Combine1ExO %>% ggplot(.,aes(x= maxPerc, y = LUPdepExt, colour = absdiff>0)) +
  geom_jitter()


```


#Model

##Create modelling dataframe

```{r}
LADprice <- prices %>%
  filter(X5!= "O") %>%
  group_by(Admin_district_code) %>%
summarise(price = mean(X2)) %>%
  mutate(pricepercent = percent_rank(price))

ModelMe <- Combine1ExO %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
  left_join(Vacants, by = "LAD11CD") %>%
  mutate(VacantsPerc = Vacants/Homes,
         LTVPerc = Vacants/Homes) %>%
  #filter out wales
  filter(!grepl("W", LAD11CD)) %>%
  mutate(Reference = as.factor(absdiff>0) ) %>%
  #scaled so that the binomial can be interpreted
  mutate(pricepercent = scale(pricepercent) %>% as.numeric,
         LUPdepExt = scale(LUPdepExt) %>% as.numeric,
         maxPerc = scale(maxPerc) %>% as.numeric,
         VacantsPerc = scale(VacantsPerc) %>% as.numeric,
         price = scale(price) %>% as.numeric,
         Extent = scale(Extent) %>% as.numeric) %>%
  mutate(Reference = (HighVal>(LUPS-HighVal)) %>% as.factor)
```


##create functions to get out model preds

```{r}
 GetAccuracy <- function(df, splits , Var ) {
  select_(df,splits) %>% flatten %>%
           map2_dbl(select_(df,Var) %>% flatten, ., ~{ augment(.x, newdata = assessment(.y)) %>%
               mutate(.fitted = factor(.fitted > 0,
                        levels = as.factor(c("FALSE", "TRUE"))))  %>%
              accuracy(., Reference, .fitted)} ) }

#If this one is used on the logistic regression I get an "incorrect number of dimensions error"
GetAccuracyForest <- function(df, splits , Var ) {
   select_(df,splits) %>% flatten %>%
map2_dbl( select_(df,Var) %>% flatten, ~{assessment(.x) %>%
   mutate(fitted = predict(.y, .) %>% .[,colnames(.)=="TRUE"],
          fitted = factor(fitted > 0,
                        levels = as.factor(c("FALSE", "TRUE")))) %>%
              accuracy(., Reference, fitted) 
}) }


```

#Create Models
```{r}

FOIFormula <- as.formula(Reference~ LUPdepExt + price + VacantsPerc)
OpenFormula <- as.formula(Reference~ Extent + price + VacantsPerc)

set.seed(4622)
Modeldf <- ModelMe  %>%
  vfold_cv(., V = 10, repeats = 10) %>%
  mutate(LogisticFOI = splits %>%
  map(.,~{ glm(FOIFormula, data = analysis(.x),binomial(link='logit'))}
        ),
  LogisticOpen = splits %>%
  map(.,~{ glm(OpenFormula, data = analysis(.x),binomial(link='logit'))}
        ),
  ForestOpen = splits %>% 
    map(., ~{rpart(OpenFormula, data=analysis(.x))})
  ) %>%
  mutate(LogFoiAcc = GetAccuracy(., "splits", "LogisticFOI"),
         LogOpenAcc = GetAccuracy(., "splits", "LogisticOpen"), 
         ForestOpenAcc = GetAccuracyForest(., "splits", "ForestOpen"))

Modeldf$LogisticOpen %>%
   map_df(., ~coefficients(.x) %>%
            as.data.frame(.) %>% rownames_to_column()) %>%
   setNames(c("key", "value")) %>%
  ggplot(aes(x= key, y = value, fill = key)) +geom_boxplot() +
  labs(title = "Coefficient values across 100 samples of 10 fold cross validation")
SaveFig("ModelCoeffs.pdf")


ModComp <- Modeldf %>%
  select(LogFoiAcc, LogOpenAcc, ForestOpenAcc) %>%
  gather
  
  ModComp %>%
  ggplot(aes(x=model, y = statistic, fill = model)) + 
  geom_boxplot()

  ModComp %>%
  group_by(model) %>%
  summarise(mean =mean(statistic))

```


#All England Bootstrap

```{r}
#Create model using all data
Mod <- ModelMe %>% 
  glm(OpenFormula, data = ., binomial(link='logit'))

LadHomes <-  EW2 %>%
  group_by(LAD11CD) %>%
  summarise(Homes = sum(Homes, na.rm = TRUE),
            Pop = sum(Pop, na.rm = TRUE))


EnglandComp <- LADDep %>% 
  select (LAD11CD, LAD11NM = Local.Authority.District.name..2013., Extent)%>% 
  left_join(., Vacants, by = "LAD11CD") %>%
  left_join(LADprice, by = c("LAD11CD" = "Admin_district_code")) %>%
  left_join( LadHomes, by = "LAD11CD") %>%
  ungroup %>%
  #left_join(Rural, by = "LAD11CD") %>%
  as.data.frame() %>%
  mutate(VacantsPerc = Vacants/Homes,
  #scaled so that the binomial can be interpreted
  pricepercent = pricepercent %>% scale %>% as.numeric,
         VacantsPerc = scale(VacantsPerc) %>% as.numeric,
         price = scale(price) %>% as.numeric,
         Extent = scale(Extent) %>% as.numeric) %>%
  mutate(Prob = predict(Mod, newdata = ., type ="response")) %>%
  #merge on the truth
  left_join(ModelMe %>% select(LAD11CD, Reference), by = "LAD11CD") %>%
  mutate(BootCol = case_when(Reference == TRUE ~1,
                             Reference == FALSE ~ 0,
                             TRUE ~ Prob),
         Comp.Type = Prob>0.5)
  
BootPopHigh <-map2(EnglandComp$Pop, EnglandComp$BootCol, 
            ~sample(c(.x, 0), size = 1000, 
                    replace = TRUE,
                    prob = c(.y, 1-.y)) %>%
              as.tibble) %>%
  bind_cols() %>%
  rowSums() %>%
  tibble(Pop=.) %>%
  mutate(PercPop = Pop/sum(EnglandComp$Pop))


BootPopHigh %>%
  ggplot(aes(x = PercPop)) +
  geom_density()



#The 95 percent confidence interval of the mean
QuantInfo<-quantile(BootPopHigh$Pop, probs = c(0.05, 0.5 ,0.95))
QuantInfo
quantile(BootPopHigh$PercPop, probs = c(0.05, 0.5 ,0.95))
#diff is 3.6M
QuantInfo[3]-QuantInfo[1]

```


