---
title: "Untitled"
author: "Jonathan Bourne"
date: "10 August 2017"
output: html_document
---

                                     

```{r setup}
setwd( "~/Dropbox/SSE/Empty Homes/EmptyHomesCode/SubCode")
source("Setup.R")

setwd(Functions)
list.files() %>% map(source)

Figures <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Empty Homes Write up/Figures"
source(file.path(CommonCode, "AuxdataLoad.R"))
```
                                     
                                     
                                     
                                     
```{r}

CombineLowUse<- function(df){ 
  df %>%
  select(LSOA_CODE, LowUse) %>%
    CalcLowUse()    
    
}                                     



test <- ChelseaLONDATA 


  
test <- ls(pattern = "CUMBRIA") %>% 
  map_df(~get(.x)) %>%
   group_by(LSOA_CODE) %>%
   summarise(LowUse = sum(LowUse, na.rm = TRUE)) %>% 
  CalcLowUse()

z<- MakeLeaflet(test)


testTower <- TowerLONDATA %>%
  CalcLowUse()


test2 <- ls(pattern = "LON") %>%
  map_df(~get(.x)) %>%   
  group_by(LSOA_CODE) %>%
   summarise(LowUse = sum(LowUse, na.rm = TRUE)) %>% 
  CalcLowUse()



test2 <-list( WestminsterLONDATA, ChelseaLONDATA, CoLLONDATA, CamdenLONDATA, TowerLONDATA) %>%
  map_df(~.x) %>%   
  group_by(LSOA_CODE) %>%
   summarise(LowUse = sum(LowUse, na.rm = TRUE)) %>% 
  CalcLowUse()

y<- MakeLeaflet(test2)

y

y2<- MakeLeaflet(TowerLONDATA)

y2

```


https://voaratinglists.blob.core.windows.net/html/rlidata.htm

```{r}

setwd(file.path(basewd,"VOA data"))

file2load <-"uk-englandwales-ndr-2017-summaryvaluations-compiled-epoch-0002-baseline-csv.csv"

test0<- read_lines(file2load, n_max=10)

test <- read_delim(file2load, delim = "*", col_names = F)

test2 <- test$`Offices And Premises` %>% table %>% as.data.frame


g1 <- test %>% filter(X1=="01")
g2 <- test %>% filter(X1=="02")


test3 <- g1$X5 %>% table %>% as.data.frame
test4 <- g2$X4 %>% table %>% as.data.frame

```


#VOA stuff

```{r}
  file2load2 <- "uk-englandwales-ndr-2017-listentries-compiled-epoch-0002-baseline-csv.csv"
test0<- read_lines(file2load2, n_max=10)

CorePstCd <- PstCdLSOA.raw %>%
  left_join(EW2, by = c("lsoa11cd" = "ECODE")) %>%
  select(Postcode,LSOA11CD= lsoa11cd, LAD11CD, LAD11NM, MSOA11CD, Pop)

setwd(file.path(basewd, "VOA data"))

CompanyData <- read_delim(file2load2, delim = "*", col_names = F) %>%
  mutate(X15 = gsub(" ", "", X15)) %>%
  left_join(., CorePstCd, by = c("X15" = "Postcode"))

#How many of the postcodes are matched?
sum(!is.na(CompanyData$LSOA11CD))/nrow(CompanyData) #this is a high number which is totally acceptable

#X10 address
#X11 is road
#X15 is postcode


#Find each type of business
LSOABiz <- CompanyData %>%
  filter(!is.na(LAD11CD)) %>%
  mutate(X6 = gsub("( AND PREMISES)|( & PREMISES)", "",X6),
         X6 = gsub("(AND PREMISES)|(& PREMISES)", "",X6)) %>%
  group_by(LSOA11CD, X6) %>%
  summarise(counts = n(),
            LAD11CD = first(LAD11CD),
            LAD11NM = first(LAD11NM),
            MSOA11CD = first(MSOA11CD)) 



FirmCounts <- LSOABiz %>%
  group_by(X6) %>%
  summarise(counts = n()) %>%
  arrange(-counts)

Dom <- FirmCounts %>%
  filter(grepl("DOMESTIC",X6))

HOLS <- FirmCounts %>%
  filter(grepl("HOLIDAY",X6))

Catering <- FirmCounts %>%
  filter(grepl("SELF CATER",X6))

Hotel <- FirmCounts %>%
  filter(grepl("(HOTEL)|(HOSTEL)",X6))

Guest <- FirmCounts %>%
  filter(grepl("(GUEST)",X6))

sum(Guest$counts)

```


#Tourism to Lups

I want to be able to plot the tourism density to deprivation and overlay the catagories and see what happens

```{r}

setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootstrapMSOA")

 LADAfford2 <- list.files(getwd()) %>%
   map_df(~readRDS(.x)) %>%
   left_join(select(IncomeEst, Yearly.income, MSOA11CD), by = "MSOA11CD") %>%
   ungroup %>%
   mutate(MSOAAffordRatio = MSOAHomesMedian/Yearly.income,
          MSOAHighVal = MSOAHomesMedian< MSOALowUseMedian, #Reference Variable
          MOSAHighLUP = MSOALowUsePerc >median(MSOALowUsePerc))  #Reference Variable
   
 
 
 %>%
   group_by(LAD11CD, ID) %>%
   summarise(LADHomesMedian = first(LADHomesMedian),
             MedianLowUse = first(LADLowUseMedian)) %>%
   group_by(LAD11CD) %>%
   summarise(LADHomesMedian = mean(LADHomesMedian, na.rm = T),
             MedianLowUse = mean(MedianLowUse, na.rm = T)) %>%
   left_join(MSOAtoLAD,., by = "LAD11CD") %>%
   filter(!is.na(LADHomesMedian)) %>% # keep only the LADs that I have data for
   left_join(., IncomeEst, by = "MSOA11CD") %>%
  group_by(LAD11CD) %>%
  summarise(Yearly.income = weighted.mean(Yearly.income, Homes),
            LADHomesMedian = weighted.mean(LADHomesMedian, Homes)) %>%
   mutate(AffordRatio = LADHomesMedian/Yearly.income,
          AffordRank = rank(AffordRatio),
          AffordRank = scale(AffordRank),
          AffordRank2 = AffordRank^2)
  

Tourism <- CompanyData %>%
  filter(!is.na(LAD11CD))%>%
  filter(grepl("(SELF CATER)|(HOLIDAY)|(HOTEL)|(HOSTEL)|(GUEST)",X6))  %>%
  mutate(Guest = grepl("(SELF CATER)|(HOLIDAY)|(GUEST)",X6),
         Hotel = grepl("(HOTEL)|(HOSTEL)",X6))
   group_by(LSOA11CD, X6) %>%
  summarise(counts = n(),
            LAD11CD = first(LAD11CD),
            LAD11NM = first(LAD11NM),
            MSOA11CD = first(MSOA11CD),
            Pop = first(Pop),
            Guest = sum(Guest),
            Hotel = sum(Hotel)) 


Tourism2 <- Tourism %>%
  group_by(LAD11CD, LAD11NM) %>%
  summarise(Tourism = sum(counts),
            Pop = sum(Pop)) 

# Only used if bootdeets two exists, which is created in the MSOAmodel rmd
testLAD <- Tourism2 %>% #
  left_join(BootDeets2,.) %>% 
  mutate(TourismDensity =Tourism/Homes,
         TourismDensityRank = percent_rank(TourismDensity)) %>%
  left_join(LADAfford2, by = "LAD11CD") %>%
  #mutate(Extent = AffordRatio) %>%
  left_join(select(LADDep, LAD11CD, Extent, Average.rank)) %>%
  mutate(ExtentRank = percent_rank(-Extent),
         ExtentRank2 = (Extent-0.5)^2,
         TourDepCat = case_when( 
           TourismDensityRank>=0.5 & ExtentRank>=0.5 ~ 1, #wealthly high tourism
           TourismDensityRank>=0.5 & ExtentRank<0.5 ~ 2, #Wealthy Low tourism
           TourismDensityRank<0.5 & ExtentRank>=0.5 ~3, #Poor High tourism
           TRUE ~ 4                                          #Poor low tourism
         ) %>% as.factor,
         Reference = Catagory==1|Catagory==2)


#This plot means we may be able to separate High low use from Low low use.
testLAD  %>%
  ggplot(aes(x= AffordRank2, y = TourismDensityRank, colour = Reference)) + geom_point()
+
  geom_hline(yintercept = 0.5) +
  geom_vline(xintercept = 0.5)


testLAD %>%
  filter(Catagory==1, TourDepCat==3) %>% select(Catagory, TourDepCat, LAD11NM)

 testLAD %>%
  filter(Catagory %in% c(3,4), TourDepCat==1) %>% select(Catagory, TourDepCat, LAD11NM)

#
#
#This model is the best for predicting LADs with high value LUPs-- Can include wales!
#
  #OpenFormula <- as.formula(Reference ~ AffordRank+ AffordRank2+ TourismDensityRank)

 
```

#local tourism.
number of hotels within 1 MSOA

```{r}

MSOAEgoListDist1 <- ego(MSOAgraph, 1) %>%map(~names(.x))
names(MSOAEgoListDist1) <- get.vertex.attribute(MSOAgraph, "name")

 NeighbourhoodQuartiles <- names(MSOAEgoListDist1) %>% map_df(~{
   
   print(.x)
   target <- MSOAEgoListDist1[[.x]]
   test <- Tourism %>%
     filter(MSOA11CD %in% target) %>%
     ungroup %>%
     summarise(
               Hotel = sum(Hotel),
               Guest = sum(Guest))

   
 }) %>%
  mutate(MSOA11CD =  names(MSOAEgoList))

 test <- NeighbourhoodQuartiles %>%
   left_join(MSOAtoLAD)
 
```


#How do I make an MSOA version? of tourism density?
2654
```{r}
MSOAtest<- CompanyData %>%
  filter(!is.na(LAD11CD))%>%
  filter(grepl("(SELF CATER)|(HOLIDAY)|(HOTEL)|(HOSTEL)(GUEST)",X6))  %>%
   group_by(LSOA11CD) %>%
  summarise(counts = n(),
            Guest = sum(grepl("(SELF CATER)|(HOLIDAY)|(GUEST)",X6)),
            Hotel = sum(grepl("(HOTEL)|(HOSTEL)",X6)),
            LAD11CD = first(LAD11CD),
            LAD11NM = first(LAD11NM),
            MSOA11CD = first(MSOA11CD),
            Pop = first(Pop)) %>%
  group_by(MSOA11CD) %>%
  summarise(Tourism = sum(counts, na.rm = T),
            Hotel= sum(Hotel, na.rm = T),
            Guest = sum(Guest, na.rm = T),
            Pop = sum(Pop),
            LAD11CD = first(LAD11CD),
            LAD11NM = first(LAD11NM)) %>% #
  left_join(BootDeetsMean,., by = "MSOA11CD") %>%
  mutate(Tourism = ifelse(is.na(Tourism), 0, Tourism),
         Guest = ifelse(is.na(Guest), 0, Guest),
         Hotel = ifelse(is.na(Hotel), 0, Hotel),
         TourismDensity =scale(Tourism/Homes),
         HotelDensity =scale(Hotel/Homes),
         GuestDensity =scale(Guest/Homes),
         TourismDensityRank = percent_rank(TourismDensity),
         TourismDensityRankV2 = rank(TourismDensity, ties.method = "max"),
         HotelDensityRank = percent_rank(HotelDensity),
         GuestDensityRank = percent_rank(GuestDensity),
         AffordRatio = scale(AffordRatio),
         AffordRatio2 = AffordRatio^2)  %>% 
  left_join(NeighbourhoodQuartiles %>% rename(Ego1Hotel= Hotel, Ego1Guest = Guest), by = "MSOA11CD") %>%
  mutate(Ego1Guest = ifelse(is.na(Ego1Guest), 0, Ego1Guest),
         Ego1Hotel = ifelse(is.na(Ego1Hotel), 0, Ego1Hotel))


ModelMSOAdf <- MSOAtest %>%
  mutate(ExtentRank = percent_rank(AffordRatio),
         TourDepCat = case_when( 
           TourismDensityRank>=0.5 & ExtentRank>=0.5 ~ 1, #wealthly high tourism
           TourismDensityRank>=0.5 & ExtentRank<0.5 ~ 2, #Wealthy Low tourism
           TourismDensityRank<0.5 & ExtentRank>=0.5 ~3, #Poor High tourism
           TRUE ~ 4                                          #Poor low tourism
         ) %>% as.factor)  %>%
   mutate(MedianPercDiff = (MSOALowUseMedian-MSOAHomesMedian)/MSOAHomesMedian,
         PercLowUse = LowUse/Homes,
         RankLowUse = percent_rank(PercLowUse),
         RankMedianDiff = percent_rank(MedianPercDiff),
         Catagory = case_when( 
           RankLowUse>=0.5 & RankMedianDiff>=0.5 ~ 1, #High low use and High price difference
           RankLowUse>=0.5 & RankMedianDiff<0.5 ~ 2, #High low Use and Low rank price difference
           RankLowUse<0.5 & RankMedianDiff>=0.5 ~3, # Low low use and high price difference
           TRUE ~ 4 #Low low use low price difference
         ) %>% as.factor,
        Reference = RankLowUse>0.5, #Catagory==1|Catagory==2,
         #Reference =MSOAHomesMedian<MSOALowUseMedian,
         spare = 1)


ModelMSOAdf   %>%
  ggplot(aes(x= AffordRank, y = TourismDensityRankV2, colour = Reference)) + geom_point() 
+
  geom_hline(yintercept = 0.5) +
  geom_vline(xintercept = 0.5)

ModelMSOAdf   %>%
  filter(Tourism == 0) %>%
  ggplot(aes(x= ExtentRank, y = LowUsePerc, colour = Catagory)) + geom_point()
+
  geom_hline(yintercept = 0.5) +
  geom_vline(xintercept = 0.5)

ModelMSOAdf  %>%
  ggplot(aes(x= RankLowUse, y = RankMedianDiff, colour = Guest>0)) + geom_point()


table(ModelMSOAdf$Guest>0, ModelMSOAdf$RankLowUse>0.5)

confusionMatrix(ModelMSOAdf$Tourism>0, ModelMSOAdf$RankLowUse>0.5)

```


#Model If a lot of LUPs

```{r}

Modeldf <- ModelMSOAdf #testLAD

OpenFormula <- as.formula(Reference ~ Guest + Hotel + AffordRatio+ AffordRatio2)

set.seed(1983)
TestResample <- 1:100 %>% map(~  resample_partition(Modeldf , c(test = 0.2, train = 0.8)))

#Make a lot of models 

ResOut <- 1:length(TestResample) %>% map_df(~{
  Mod2 <- Modeldf  %>%
  mutate(Reference = as.factor(Reference)) %>%
  slice(as.integer(TestResample[[.x]]$train)) %>%
  glm(formula = OpenFormula, data = ., family=binomial(link='logit'))


preds2<- Modeldf  %>%
  mutate(Reference = as.factor(Reference)) %>%
  slice(as.integer(TestResample[[.x]]$test)) %>%
predict(Mod2, ., type = "response")

ConfOut<-Modeldf  %>%
  mutate(Reference = as.factor(Reference)) %>%
  slice(as.integer(TestResample[[.x]]$test)) %>%
  pull(Reference) %>%
confusionMatrix(.,preds2>0.5)

ConfOut$overall %>% t %>% data.frame() %>% as.tibble

  
})

test <- tibble(truth = ConfOut, estimate = as.factor(preds2>0.5))
conf_mat(test, truth, estimate) %>%summary(wide= T)

MODOut <- 1:length(TestResample) %>% map_df(~{
  Mod2 <- Modeldf  %>%
  mutate(Reference = as.factor(Reference)) %>%
  slice(as.integer(TestResample[[.x]]$train)) %>%
  glm(formula = OpenFormula, data = ., family=binomial(link='logit'))%>%
    tidy

})

ggplot(MODOut, aes(x = term, y = estimate)) + geom_boxplot()

#
#        TREEEEEEEEEEEEEEEEEE
# 
OpenFormula <- as.formula(Reference ~ TourismDensityRank + AffordRatio+ AffordRatio2)


library(ranger)
ResOut <- 1:length(TestResample) %>% map_df(~{
  print(.x)
  Mod2 <- Modeldf  %>%
  mutate(Reference = as.factor(Reference)) %>%
  slice(as.integer(TestResample[[.x]]$train)) %>%
  ranger(formula = OpenFormula, data = . )


preds2<- Modeldf  %>%
  mutate(Reference = as.factor(Reference)) %>%
  slice(as.integer(TestResample[[.x]]$test)) %>%
predict(Mod2, ., type = "response")
preds2 <- preds2$predictions

ConfOut<-Modeldf  %>%
  mutate(Reference = as.factor(Reference)) %>%
  slice(as.integer(TestResample[[.x]]$test)) %>%
  pull(Reference) %>%
confusionMatrix(.,preds2)

ConfOut$overall %>% t %>% data.frame() %>% as.tibble

  
})

sum(ResOut$Accuracy>ResOut$AccuracyNull)/nrow(ResOut)
mean(ResOut$Accuracy)

#The models are significantly greater than the null model when using a paired t-test.
t.test(ResOut$Accuracy,ResOut$AccuracyNull, alternative = "greater", paired = T)

ResOut %>%
  ggplot(aes(x = (Accuracy - AccuracyNull))) + geom_density()
  

```



#Look at Westminster

```{r}

West <- LSOABiz %>5
  filter(LAD11CD=="E09000033")


Catering <- West %>%
  filter(grepl("(SELF CATER)|(HOLIDAY)|(HOTEL)|(HOSTEL)(GUEST)",X6))

sum(Catering$counts)


test <- list(HammersmithLONDATA, WestminsterLONDATA, ChelseaLONDATA, CoLLONDATA, CamdenLONDATA, LambethLONDATA) %>% 
  map_df(~.x) %>%
  group_by(LAD11CD) %>%
  summarise(
    LAD11NM =first(LAD11NM),
    LowUse = sum(LowUse, na.rm= T),
    Homes = sum(Homes, na.rm= T),
    Pop = sum(Pop, na.rm= T)
            ) %>%
  filter(Homes >2000) %>%
  mutate(LowUseH = LowUse/Homes,
         LowUseP = LowUse/Pop)

```


```{r}

SalesLAD <- prices %>%
  group_by(Admin_district_code) %>%
    filter(X5 %in% c("D", "S", "T", "F")) %>%
    summarise(sales = n(), 
            mean = mean(X2, na.tm = TRUE))
 
SalesWard <- prices %>%
  group_by(Admin_ward_code) %>%
    filter(X5 %in% c("D", "S", "T", "F")) %>%
    summarise(sales = n(), 
            mean = mean(X2, na.tm = TRUE))

SalesWard %>% ggplot(aes(x = sales, y = mean )) + geom_point()
 
```

```{r}
test <- ChelseaLONDATA %>%
            # select(WardLowUsePerc, WardLowUse) %>%
             mutate( WardLowUsePerc = ifelse(is.na(WardLowUsePerc),0, WardLowUsePerc)) %>%
             summarise( maxPerc = max(WardLowUsePerc, na.rm=TRUE),
                        minPerc = min(WardLowUsePerc, na.rm=TRUE),
                        diffPerc = maxPerc-minPerc,
                        max = max(WardLowUse, na.rm=TRUE),
                        min = min(WardLowUse, na.rm=TRUE),
                        diff = max-min,
                        mean = mean(WardLowUse, na.rm=TRUE),
                        median = median(WardLowUse, na.rm=TRUE),
                        LAD = sub("DATA", "", "ChelseaLONDATA"),
                        TurnoverPerc = sum(PercTurnover*Homes, na.rm = TRUE)/sum(Homes, na.rm = TRUE),
                        LUPTurnoverPerc = sum(PercTurnover*LowUse, na.rm = TRUE)/sum(LowUse, na.rm = TRUE)
                        )
```

#Match VOA to offshore test work

```{r}

setwd(DataFolder)

Offshore <- read_excel("OV_FULL_2016_02 (with PEP database for lookup).xlsx", sheet = "OV_FULL_2016_02")


test <- Offshore %>%
  filter(!is.na(Price_Paid))

Offshore$Property_Address %>% head(20)


Offshore2 <- Offshore %>%
    select(Property_Address, Postcode) %>%
    mutate(Postcode = gsub(" ", "",Postcode)) 



NumberofPostocodes <-CompanyData %>% filter(X15 %in% Offshore2$Postcode) %>%
  group_by(X15) %>%
  summarise(counts = n()) %>%
  left_join(Offshore2, ., by = c("Postcode" = "X15")) %>%
  filter(!is.na(Postcode))
  

#20,000 flat or apartments
grepl("^flat|^apartment|^penthouse", Offshore2$Property_Address, ignore.case = T) %>% table
ffshore$Property_Address
grepl("suite", Offshore2$Property_Address, ignore.case = T) %>% table
grepl("unit", Offshore2$Property_Address, ignore.case = T) %>% table

test <- Offshore2 %>%
  filter(grepl("unit", Offshore2$Property_Address, ignore.case = T))


#need another regex which looks at number and if followed by apartement etc uses the number as the flat number
Flatregex <- "(the.+)?(flat|apartment|penthouse)(s)?(\\s(no)?(\\S+?)(\\s|,)(\\s?(to|-)\\s?.+?(\\s|,))?|,)"

Flats <- Offshore2 %>%
  filter(grepl(Flatregex , Property_Address, ignore.case = T))%>%
  mutate(FlatNumber = str_extract(tolower(Property_Address), 
            Flatregex) %>%
           sub("\\s$|,$", "", .)
) 

(flat|apartment|penthouse)(s)? 

# (the.+)?(flat|apartment|penthouse)(s)?(\\s(.+?)(\\s|,)(\\s?(to|-)\\s?.+?(\\s|,))?|,)
# 
# some flats start with a "the eastern" or "the penthouse" this is optional
# (the.+)?
# 
# the main expression it has to say this! optional "s" on the end
# (flat|apartment|penthouse)(s)?
#
#the additional matching characteristics these come either side of and or statement
# ((s)?\\s(\S+?)(\\s|,)(\\s?(to|-)\\s?.+?(\\s|,))?|,)
# (A|B)
# 
# 
# A = \\s(\S+?)(\\s|,)(\\s?(to|-)\\s?.+?(\\s|,))?
# A = (A1)(A2)
# 
# space followed by anything that is not whitespace followed by a space or a comma this extracts the flat number eg "flat c"
# A1 = \\s(\S+?)(\\s|,)
# 
# optional space then either "to" or "-" followed by optional space followed by some characters followed by space or comma. This is to catch things like "flats 1 to 5" or flat 4-6
# A2 = (\\s?(to|-)\\s?.+?(\\s|,))?
# 
# This is simple some are simply called "flat"  or "the penthouse" this catches those
# B = ,



Flats <- Flats%>%
  mutate(leng = str_split(Flats$Property_Address, ",", n = 2) %>% 
  map_chr(~length(.x)) 
  ) %>% 
  filter(leng == 2) %>%
  mutate( address2 = str_split(Property_Address, ",", n = 2) %>% 
  map_chr(~.x[[2]]) %>% 
    gsub("\\s*\\([^\\)]+\\)", "",.)%>% 
    gsub(" and .+", "",.)
  )

Flats2 <- Flats %>%
  group_by(address2) %>%
  summarise(counts = n()) %>%
  arrange(-counts) 

#Use Dolphin Square to extract house names
test <- Flats2 %>%
  filter(grepl("Dolphin Square", address2, ignore.case = TRUE)) %>%
  mutate(address2 = str_extract(tolower(address2), "([a-z0-9]+)\\s(house)"))

sum(test$counts)


test <- Offshore2 %>%
  filter(grepl("^[a-z]+( [a-z])* house", Offshore2$Property_Address, ignore.case = T))

#car parks
grepl("car", Offshore2$Property_Address, ignore.case = T) %>% table

ParkingSpaces <- Offshore2 %>%
  filter(grepl("^car |^park", Offshore2$Property_Address, ignore.case = T))

#random land
grepl("^land", Offshore2$Property_Address, ignore.case = T) %>% table


test <- Offshore2 %>%
  filter(grepl("^land", Offshore2$Property_Address, ignore.case = T))



Roadnames <- unique(CompanyData$X11) %>% 
  gsub(" north| south| east| west", "",., ignore.case = TRUE) %>% 
  word(.,-1) %>% data_frame(Endings = .) %>%
  group_by(Endings) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  mutate(cumsum = cumsum(count),
         cumperc = cumsum/sum(count))

#A list of road names to remove as they cause problems
removeNames <- "park house buildings green end farm estate court bridge hall drove" %>% str_split(., " ", simplify = TRUE)

#match the top most occuring endings to the offshore list and get the counts
TopRoadEndings <- Roadnames$Endings[1:50] %>%  map_dbl(~ sum(grepl(.x, Offshore$Property_Address, ignore.case = TRUE)))

#arrange in order of occurnace and remove the tricky ones
Road2 <- Roadnames[1:50,] %>% mutate(occs = TopRoadEndings) %>%
  arrange(-occs) %>%
  mutate(Endings = tolower(Endings)) %>%
  filter(!(Endings %in% removeNames)) %>%
  mutate(cumsum = cumsum(occs))

#need to include thigs like gate

#create the regex string to match
Wordswithapotrophes <- paste0("(( \\w+)('s)?)+ (",
                              paste(c(Road2$Endings, 
                                      "( \\w+)+(way|gate,)",
                                      "knightsbridge",
                                      "holland"
                                      ),  collapse = "|"),")")
roadmatchregex <- paste0("(([0-9]+([a-z])?))?", Wordswithapotrophes)

paste0("(( \\w+)('s)?)+(gate,)")


#This is used in the next code cleaning block it is done here to keep the code easier to read
StreetNum <- str_extract(tolower(Offshore2$Property_Address), roadmatchregex )


Offshore3 <- Offshore2 %>% 
  mutate(
    Property_Address =  gsub(" \\(.+?\\)", "", Property_Address), #remove anything in brackets e.g postcodes
    #Label some classes
    class = case_when( 
    grepl(Flatregex, Property_Address, ignore.case = T) ~ "domestic",
    grepl("^car |^park", Property_Address, ignore.case = T) ~"parking space",
    grepl("^land", Property_Address, ignore.case = T) ~ "land",
    grepl("^[a-z]+( [a-z])* cottage", Property_Address, ignore.case = T) ~"domestic",
    grepl("(^[0-9]+([a-z])?)(( \\w+)('s)?)+ (court|villas|mansions)", Property_Address, ignore.case = T) ~"domestic",
    TRUE ~ "unknown"
  )) %>%
  #Do Streets
  mutate( Street = gsub("([0-9]+([a-z])?)", "", StreetNum),
          Streetnumber =gsub("([a-z])+", "", StreetNum, ignore.case = T),
          Street = case_when(
      !is.na(Street) ~ Street, #if not NA keep as is otherwise...
      TRUE ~ str_extract(tolower(Property_Address), Wordswithapotrophes ) #no street number
    ),
    Street = case_when(
            grepl("^land", Property_Address, ignore.case = T) ~ 
        str_extract(tolower(Property_Address), paste0("(of|at)", Wordswithapotrophes) ) %>%
          gsub("of |at ", "",.), #begins with land about 13k
        TRUE ~ Street
        
    ) %>% gsub(" (and|to) ", "", .)
    ) %>%
  #sorting houses
  mutate(
    HouseName  = str_extract(tolower(Property_Address), "^([a-z]+)( [a-z]+)* (house|court|farm|villa|cottage|lodge)(s)?") %>%
      ifelse(grepl("^land",.), NA,.)
 
    ) %>%
#Trim whitspace
mutate(Street = trimws(Street))

  

  
  #random
    OffshoreHouse <- Offshore3 %>%
  filter(grepl("house", tolower(Property_Address)), class =="unknown") 
 
        OffshoreHouse <- Offshore %>%
  filter(grepl("house", tolower(Property_Address))) 
    
    
    #why are there no overlaps?
    #look at needham house
       
    CompanyHouse <- CompanyData %>%
      mutate(House = tolower(X8)) %>%
  filter(grepl("house", House)) 
    
 test <-    CompanyHouse %>%
      filter(grepl( "mansions",  House, ignore.case = T))

 #this matchers
   MMhouse <-    OffshoreHouse %>%
      filter(grepl( "Matthew Murray House",  Property_Address, ignore.case = T))
   
#Darcy matches
Darcy <-    CompanyHouse %>%
      filter(grepl( "Darcy House",  House, ignore.case = T))
  
#hotel where some rooms are owned offshore
  Needham <-    OffshoreHouse %>%
      filter(grepl( "Needham",  Property_Address, ignore.case = T))
  
  #All the directorss are registered to the same place and have no digital foot print
  Debenham <-    OffshoreHouse %>%
      filter(grepl( "debenham",  Property_Address, ignore.case = T))  

    
  
    %>%
    filter(class == "unknown")

table(test$class)


test <- Offshore3 %>% 
  filter(Offshore3$Street %in% tolower(CompanyData$X11)) %>%
  filter(!is.na(Street), class == "unknown") %>%
  group_by(Street) %>%
  summarise(counts = n())


```

#Split out VOA addresses

```{r}

rm(columnnames)


#create street and number split out like for offshore
CompanyData2 <- CompanyData %>%
  rename(Property_Address = X8)

StreetNum <- str_extract(tolower(CompanyData2$Property_Address), roadmatchregex )

CompanyData2 <- CompanyData2 %>%
    mutate( Street = gsub("([0-9]+([a-z])?)", "", StreetNum),
          Streetnumber =gsub("([a-z])+", "", StreetNum, ignore.case = T),
          Street = case_when(
      !is.na(Street) ~ Street, #if not NA keep as is otherwise...
      TRUE ~ str_extract(tolower(Property_Address), Wordswithapotrophes ) #no street number
    ),
    Street = case_when(
            grepl("^land", Property_Address, ignore.case = T) ~ 
        str_extract(tolower(Property_Address), paste0("(of|at)", Wordswithapotrophes) ) %>%
          gsub("of |at ", "",.), #begins with land about 13k
        TRUE ~ Street
        
    ) %>% gsub(" (and|to) ", "", .)
    )


#overlapping street names
sum(unique(Offshore3$Street) %in% tolower(unique(CompanyData$X11)))

sum(unique(Offshore3$HouseName) %in% tolower(unique(CompanyData$X25)))

test <- Offshore3 %>%
  filter(HouseName %in% tolower(unique(CompanyData$X25)), !is.na(HouseName))

#match house name and street
StreetHouseComp <- tolower(paste(CompanyData$X11,CompanyData$X25)) %>% unique
StreetHouseOffshore <- tolower(paste(Offshore3$Street,Offshore3$HouseName))[!is.na(Offshore3$HouseName)] %>% unique


#Actual companies!
CompMatch <- CompanyData %>%
  filter(  tolower(paste(X11,X25)) %in% StreetHouseOffshore, is.na(X23)  )

OffshoreMatch <- Offshore3 %>%
  filter(paste(Street,HouseName) %in% StreetHouseComp, !is.na(HouseName))

OffshoreMatch2 <- Offshore3 %>%
  mutate(test = paste(Street,HouseName))
"matthew murray house"
name <- "matthew murray house"

Companyinfo <- CompanyData %>%
  filter(grepl(name, tolower(X25), ignore.case = T))

OffshoreInfo <-Offshore3 %>%
  filter(grepl(name, HouseName, ignore.case = T))

```

#match lsoa for offshore postcodes

```{r}
test <- Offshore %>%
  filter(!is.na(Postcode)) %>%
  mutate(Postcode = gsub(" ", "", Postcode)) %>%
  left_join(., CorePstCd, "Postcode")

table(is.na(test$LSOA11CD))


test2 <- test %>%
  filter(!is.na(LSOA11CD)) %>%
  group_by(LSOA11CD) %>%
  summarise(counts = n(),
            LAD11CD = first(LAD11CD),
            LAD11NM = first(LAD11NM),
            Admin_ward_code = first(Admin_ward_code),
            WD16NM = first(WD16NM)) %>%
  arrange(desc(counts))


examin <- test %>% 
  filter(LSOA11CD =="E01006854")

table(examin$Proprietor_Name_1)
```


#Improve geoloacation

```{r}
setwd(file.path(DataFolder, "GeoNames"))

columnnames <- "geonameid
name
asciiname
alternatenames
latitude
longitude
feature class
feature code
country code
cc2
admin1 code
admin2 code 
admin3 code
admin4 code
population
elevation
dem
timezone
modification date " %>% str_split(., "\n", simplify = T) %>% trimws

GeoNames <- read_tsv("GB.txt", col_names = FALSE) %>%
  setNames(columnnames)

MaxMind <- read_csv("worldcitiespop.txt")

test <- MaxMind %>%
  filter(Country == "gb")

test %>%
  filter(grepl("queens", City, ignore.case = TRUE) )

test <- GeoNames %>%
filter(grepl("queens", name, ignore.case = TRUE) )

```


#Unique Company's


```{r}

CompCounts <- Offshore %>%
select(c(grep("Proprietor_Name",names(Offshore)) )) %>% unlist %>%
  data.frame(comp = .) %>%
  group_by(comp) %>%
  summarise(counts = n()) %>%
  filter(!is.na(comp))

sum(CompCounts$counts)

plot(density(CompCounts$counts))

test <- CompCounts %>%
  filter(grepl("trustee", comp, ignore.case = T))

```



```{r}

Flats3<- Flats %>% left_join(PstCdLSOA.raw)%>%
   group_by(LSOA11CD) %>%
  summarise(Total = n()) %>%
#  left_join(EW2, by = c("LSOA11CD" = "ECODE")) %>%
  rename(LSOA_CODE = LSOA11CD)


Flats4 <- Flats3 %>% group_by(LAD11NM) %>%
  summarise(Total = sum(Total))


test <-ls(pattern = "LON") %>% 
  map_df(~get(.x))  %>%
   group_by(LSOA_CODE) %>%
   summarise(LowUse = sum(LowUse, na.rm = TRUE)) %>% 
  CalcLowUse() %>%
  select(LSOA_CODE, Homes, LowUse,LAD11NM:MeanPrice) %>%
  left_join(filter(Flats3, !is.na(LSOA_CODE))) %>%
  mutate(Total = ifelse(is.na(Total), 0, Total),
         LowUsePerc = round(Total/Homes,3)*100)


sum(test$Total)


test %>% 
  group_by(LAD11NM) %>%
  summarise(Total = sum(Total)) %>%
  mutate(perc = round(Total/sum(Total),3)) %>%
  arrange(-perc)

g <- MakeLeaflet(test, type = "jyg", bins = c(0, 5,10,15,100))


Dolph<- Offshore %>%
  filter(grepl("dolphin square", Offshore$Property_Address, ignore.case = T))

```


UK has 20k flats owned by offshore companies. 75% are in #London and of those 43% are in #Westminster.


#London Flats owned by offshore companies as a % of all homes. 43% are in #Westminster, 20% in #RBKC

#London has 14k flats owned by offshore companies. 43% are in #Westminster, 20% in #RBKC. Map % of ALL homes



#Address fixing


```{r}

library(poster)
test <- parse_addr(Offshore$Property_Address)


test <- paste(Offshore$Property_Address, "United Kingdom", sep= ", ") %>%
   normalise_addr %>%
  parse_addr


#\([a-z0-9]+\s[a-z0-9]+

    test1 <-paste(Offshore$Property_Address, "United Kingdom", sep= ", ") 
  
    test2 <- paste(Offshore$Property_Address, "United Kingdom", sep= ", ") %>%
     gsub(" \\(.+?\\)", "", .) %>%
            #gsub("(\\s\\()(?=[a-z0-9]+\\s[a-z0-9]+)", ", ", ., ignore.case = TRUE, perl= TRUE) %>%
      gsub("(and )?(car )?(park(ing)?)( space(\\w)?)?", "", .) %>%
    normalise_addr %>%
    parse_addr

    
    test3 <- test2 %>% mutate(postal_code = gsub(" ", "", Offshore$Postcode)) %>%
      filter(!is.na(postal_code))
    
    test4 <- test3 %>%
      group_by(postal_code, road) %>%
      summarise(counts = n())
    
        CompPostRoad <- CompanyData %>%
      group_by(X11, X15) %>%
      summarise(counts = n())
    
CompAddress <- paste(CompanyData$X8, CompanyData$X15, "United Kingdom", sep =",") %>%
    normalise_addr %>%
    parse_addr

test5 <- CompAddress %>%
      group_by(postal_code, road) %>%
      summarise(counts = n())


  sum(paste(test4$road, test4$postal_code) %in% paste(test5$road, test5$postal_code))

#savved to VOA folder    
#saveRDS(CompAddress, "CompanyAddresseslibpostal.rds")

    test2[1:20] 
    Offshore$Property_Address[1:20]


    sum(grepl("gate", Offshore$Property_Address, ignore.case = TRUE))




test <- Offshore %>%
  select(Property_Address) %>%
  mutate(Property_Address = gsub(" \\(.+?\\)", "", Property_Address) )%>%
  filter(grepl("(and )?(car )?park(ing)? space(s)?|(and )?car park(ing)?( space(s)?)?", Property_Address, ignore.case = T))


test <- Offshore %>%
  select(Property_Address) %>%
  mutate(Property_Address = gsub(" \\(.+?\\)", "", Property_Address) )%>%
  filter(grepl(" bridge", Property_Address, ignore.case = T))

test[1:20,1]

removeNames <- "park house buildings green end farm estate court bridge hall" %>% str_split(., " ", simplify = TRUE)

TopRoadEndings <- Roadnames$Endings[1:50] %>%  map_dbl(~ sum(grepl(.x, Offshore$Property_Address, ignore.case = TRUE)))

Road2 <- Roadnames[1:50,] %>% mutate(occs = TopRoadEndings) %>%
  arrange(-occs) %>%
  mutate(Endings = tolower(Endings)) %>%
  filter(!(Endings %in% removeNames)) %>%
  mutate(cumsum = cumsum(occs))

length(Offshore$Property_Address) 




table(is.na(StreetNum))

```


